---
title: "AXH_DESeq-contrasts_Pdam"
author: "Mike Connelly"
date: "9/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/computing/scripts/EAPSI_HW-WT-master/")
library(DESeq2)
library(VennDiagram)
```
```{r}
resultsNames(dds_anti)
resultsNames(dds_heat)
resultsNames(dds_anti.heat)
resultsNames(dds_antixheat)
```

##Overall model results contrasts between individual treatments and control samples

### Antibiotics vs. Control
```{r}
res_anti_ctrl <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics", "control"))
res_anti_ctrl$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti_ctrl$IDGeneInfo <- as.character(res_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_anti_ctrl[order(res_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_anti_ctrl.csv")
ressig_anti_ctrl <- subset(res_anti_ctrl, padj<0.01)
ressig_anti_ctrl_up <- subset(res_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_anti_ctrl_dn <- subset(res_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti_ctrl[order(ressig_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti_ctrl.csv")
write.csv(as.data.frame(ressig_anti_ctrl_up[order(ressig_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti_ctrl_dn[order(ressig_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti_ctrl_dn.csv")
colnames(res_anti_ctrl)
summary(res_anti_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt-e
```

### Heat vs. Control
```{r}
res_heat_ctrl <- results(dds_antixheat, contrast = c("Treatment", "Heat", "control"))
res_heat_ctrl$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_heat_ctrl$IDGeneInfo <- as.character(res_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_heat_ctrl[order(res_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_heat_ctrl.csv")
ressig_heat_ctrl <- subset(res_heat_ctrl, padj<0.01)
ressig_heat_ctrl_up <- subset(res_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_heat_ctrl_dn <- subset(res_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_heat_ctrl[order(ressig_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_heat_ctrl.csv")
write.csv(as.data.frame(ressig_heat_ctrl_up[order(ressig_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_heat_ctrl_dn[order(ressig_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_heat_ctrl_dn.csv")
colnames(res_heat_ctrl)
summary(res_heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt-e
```

### Antibiotics.Heat vs. Control
```{r}
res_anti.heat_ctrl <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_anti.heat_ctrl$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti.heat_ctrl$IDGeneInfo <- as.character(res_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_anti.heat_ctrl[order(res_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_anti.heat_ctrl.csv")
ressig_anti.heat_ctrl <- subset(res_anti.heat_ctrl, padj<0.01)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti.heat_ctrl_dn.csv")
colnames(res_anti.heat_ctrl)
summary(res_anti.heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti.heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti.heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti.heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt-e
```

### Antibiotics.Heat vs. Antibiotics
```{r}
res_anti.heat_anti <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_anti.heat_anti$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti.heat_anti$IDGeneInfo <- as.character(res_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_anti.heat_anti[order(res_anti.heat_anti$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_anti.heat_anti.csv")
ressig_anti.heat_ctrl <- subset(res_anti.heat_anti, padj<0.01)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti.heat_anti_dn.csv")
colnames(res_anti.heat_anti)
summary(res_anti.heat_anti)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti.heat_anti.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti.heat_anti_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti.heat_anti_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt-e
```

### Antibiotics.Heat vs. Heat
```{r}
res_anti.heat_heat <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_anti.heat_heat$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti.heat_heat$IDGeneInfo <- as.character(res_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_anti.heat_heat[order(res_anti.heat_heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_anti.heat_heat.csv")
ressig_anti.heat_ctrl <- subset(res_anti.heat_heat, padj<0.01)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti.heat_heat_dn.csv")
colnames(res_anti.heat_heat)
summary(res_anti.heat_heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_anti.heat_heat.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_anti.heat_heat_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_anti.heat_heat_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt-e
```

## Results contrasts between different coral genotypes

### Houwan1 vs. Houwan2
```{r}
res_HW1_HW2 <- results(dds_antixheat, contrast = c("Colony", "HW1", "HW2"))
res_HW1_HW2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW1_HW2$IDGeneInfo <- as.character(res_HW1_HW2$IDGeneInfo)
write.csv(as.data.frame(res_HW1_HW2[order(res_HW1_HW2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_HW2.csv")
ressig_HW1_HW2 <- subset(res_HW1_HW2, padj<0.01)
ressig_HW1_HW2_up <- subset(res_HW1_HW2, padj<0.01 & log2FoldChange>0)
ressig_HW1_HW2_dn <- subset(res_HW1_HW2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_HW2[order(ressig_HW1_HW2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_HW2.csv")
write.csv(as.data.frame(ressig_HW1_HW2_up[order(ressig_HW1_HW2_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_HW2_up.csv")
write.csv(as.data.frame(ressig_HW1_HW2_dn[order(ressig_HW1_HW2_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_HW2_dn.csv")
colnames(res_HW1_HW2)
summary(res_HW1_HW2)
```

### Houwan1 vs. Wanglitung1
```{r}
res_HW1_WT1 <- results(dds_antixheat, contrast = c("Colony", "HW1", "WT1"))
res_HW1_WT1$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW1_WT1$IDGeneInfo <- as.character(res_HW1_WT1$IDGeneInfo)
write.csv(as.data.frame(res_HW1_WT1[order(res_HW1_WT1$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_WT1.csv")
ressig_HW1_WT1 <- subset(res_HW1_WT1, padj<0.01)
ressig_HW1_WT1_up <- subset(res_HW1_WT1, padj<0.01 & log2FoldChange>0)
ressig_HW1_WT1_dn <- subset(res_HW1_WT1, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_WT1[order(ressig_HW1_WT1$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_WT1.csv")
write.csv(as.data.frame(ressig_HW1_WT1_up[order(ressig_HW1_WT1_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_WT1_up.csv")
write.csv(as.data.frame(ressig_HW1_WT1_dn[order(ressig_HW1_WT1_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_WT1_dn.csv")
colnames(res_HW1_WT1)
summary(res_HW1_WT1)
```

### Houwan1 vs. Wanglitung2
```{r}
res_HW1_WT2 <- results(dds_antixheat, contrast = c("Colony", "HW1", "WT2"))
res_HW1_WT2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW1_WT2$IDGeneInfo <- as.character(res_HW1_WT2$IDGeneInfo)
write.csv(as.data.frame(res_HW1_WT2[order(res_HW1_WT2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_WT2.csv")
ressig_HW1_WT2 <- subset(res_HW1_WT2, padj<0.01)
ressig_HW1_WT2_up <- subset(res_HW1_WT2, padj<0.01 & log2FoldChange>0)
ressig_HW1_WT2_dn <- subset(res_HW1_WT2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_WT2[order(ressig_HW1_WT2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_WT2.csv")
write.csv(as.data.frame(ressig_HW1_WT2_up[order(ressig_HW1_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_WT2_up.csv")
write.csv(as.data.frame(ressig_HW1_WT2_dn[order(ressig_HW1_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_WT2_dn.csv")
colnames(res_HW1_WT2)
summary(res_HW1_WT2)
```

### Houwan2 vs. Wanglitung1
```{r}
res_HW2_WT1 <- results(dds_antixheat, contrast = c("Colony", "HW2", "WT1"))
res_HW2_WT1$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW2_WT1$IDGeneInfo <- as.character(res_HW2_WT1$IDGeneInfo)
write.csv(as.data.frame(res_HW2_WT1[order(res_HW2_WT1$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW2_WT1.csv")
ressig_HW2_WT1 <- subset(res_HW2_WT1, padj<0.01)
ressig_HW2_WT1_up <- subset(res_HW2_WT1, padj<0.01 & log2FoldChange>0)
ressig_HW2_WT1_dn <- subset(res_HW2_WT1, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_WT1[order(ressig_HW2_WT1$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_WT1.csv")
write.csv(as.data.frame(ressig_HW2_WT1_up[order(ressig_HW2_WT1_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_WT1_up.csv")
write.csv(as.data.frame(ressig_HW2_WT1_dn[order(ressig_HW2_WT1_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_WT1_dn.csv")
colnames(res_HW2_WT1)
summary(res_HW2_WT1)
```

### Houwan2 vs. Wanglitung2
```{r}
res_HW2_WT2 <- results(dds_antixheat, contrast = c("Colony", "HW2", "WT2"))
res_HW2_WT2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW2_WT2$IDGeneInfo <- as.character(res_HW2_WT2$IDGeneInfo)
write.csv(as.data.frame(res_HW2_WT2[order(res_HW2_WT2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW2_WT2.csv")
ressig_HW2_WT2 <- subset(res_HW2_WT2, padj<0.01)
ressig_HW2_WT2_up <- subset(res_HW2_WT2, padj<0.01 & log2FoldChange>0)
ressig_HW2_WT2_dn <- subset(res_HW2_WT2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_WT2[order(ressig_HW2_WT2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_WT2.csv")
write.csv(as.data.frame(ressig_HW2_WT2_up[order(ressig_HW2_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_WT2_up.csv")
write.csv(as.data.frame(ressig_HW2_WT2_dn[order(ressig_HW2_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_WT2_dn.csv")
colnames(res_HW2_WT2)
summary(res_HW2_WT2)
```

### Wanglitung1 vs. Wanglitung2
```{r}
res_WT1_WT2 <- results(dds_antixheat, contrast = c("Colony", "WT1", "WT2"))
res_WT1_WT2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_WT1_WT2$IDGeneInfo <- as.character(res_WT1_WT2$IDGeneInfo)
write.csv(as.data.frame(res_WT1_WT2[order(res_WT1_WT2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT1_WT2.csv")
ressig_WT1_WT2 <- subset(res_WT1_WT2, padj<0.01)
ressig_WT1_WT2_up <- subset(res_WT1_WT2, padj<0.01 & log2FoldChange>0)
ressig_WT1_WT2_dn <- subset(res_WT1_WT2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_WT2[order(ressig_WT1_WT2$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_WT2.csv")
write.csv(as.data.frame(ressig_WT1_WT2_up[order(ressig_WT1_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_WT2_up.csv")
write.csv(as.data.frame(ressig_WT1_WT2_dn[order(ressig_WT1_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_WT2_dn.csv")
colnames(res_WT1_WT2)
summary(res_WT1_WT2)
```

## Colony-specific treatment contrasts results
### Houwan1
#### Antibiotics vs. Control
```{r}
res_HW1_anti_ctrl <- results(dds_HW1, contrast = c("Treatment", "Antibiotics", "control"))
res_HW1_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti_ctrl$IDGeneInfo <- as.character(res_HW1_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti_ctrl[order(res_HW1_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_anti_ctrl.csv")
ressig_HW1_anti_ctrl <- subset(res_HW1_anti_ctrl, padj<0.01)
ressig_HW1_anti_ctrl_up <- subset(res_HW1_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti_ctrl_dn <- subset(res_HW1_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti_ctrl[order(ressig_HW1_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti_ctrl.csv")
write.csv(as.data.frame(ressig_HW1_anti_ctrl_up[order(ressig_HW1_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW1_anti_ctrl_dn[order(ressig_HW1_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti_ctrl_dn.csv")
colnames(res_HW1_anti_ctrl)
summary(res_HW1_anti_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti_ctrl_dn_ID.txt-e
```
#### Heat vs. Control
```{r}
res_HW1_heat_ctrl <- results(dds_HW1, contrast = c("Treatment", "Heat", "control"))
res_HW1_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_heat_ctrl$IDGeneInfo <- as.character(res_HW1_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_heat_ctrl[order(res_HW1_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_heat_ctrl.csv")
ressig_HW1_heat_ctrl <- subset(res_HW1_heat_ctrl, padj<0.01)
ressig_HW1_heat_ctrl_up <- subset(res_HW1_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW1_heat_ctrl_dn <- subset(res_HW1_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_heat_ctrl[order(ressig_HW1_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW1_heat_ctrl_up[order(ressig_HW1_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW1_heat_ctrl_dn[order(ressig_HW1_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_heat_ctrl_dn.csv")
colnames(res_HW1_heat_ctrl)
summary(res_HW1_heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Control
```{r}
res_HW1_anti.heat_ctrl <- results(dds_HW1, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_HW1_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti.heat_ctrl$IDGeneInfo <- as.character(res_HW1_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti.heat_ctrl[order(res_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_anti.heat_ctrl.csv")
ressig_HW1_anti.heat_ctrl <- subset(res_HW1_anti.heat_ctrl, padj<0.01)
ressig_HW1_anti.heat_ctrl_up <- subset(res_HW1_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti.heat_ctrl_dn <- subset(res_HW1_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl[order(ressig_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_up[order(ressig_HW1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_dn[order(ressig_HW1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti.heat_ctrl_dn.csv")
colnames(res_HW1_anti.heat_ctrl)
summary(res_HW1_anti.heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti.heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti.heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti.heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Antibiotics
```{r}
res_HW1_anti.heat_anti <- results(dds_HW1, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_HW1_anti.heat_anti$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti.heat_anti$IDGeneInfo <- as.character(res_HW1_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti.heat_anti[order(res_HW1_anti.heat_anti$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_anti.heat_anti.csv")
ressig_HW1_anti.heat_ctrl <- subset(res_HW1_anti.heat_anti, padj<0.01)
ressig_HW1_anti.heat_ctrl_up <- subset(res_HW1_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti.heat_ctrl_dn <- subset(res_HW1_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl[order(ressig_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_up[order(ressig_HW1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_dn[order(ressig_HW1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti.heat_anti_dn.csv")
colnames(res_HW1_anti.heat_anti)
summary(res_HW1_anti.heat_anti)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti.heat_anti.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti.heat_anti_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti.heat_anti_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_anti_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Heat
```{r}
res_HW1_anti.heat_heat <- results(dds_HW1, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_HW1_anti.heat_heat$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti.heat_heat$IDGeneInfo <- as.character(res_HW1_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti.heat_heat[order(res_HW1_anti.heat_heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW1_anti.heat_heat.csv")
ressig_HW1_anti.heat_ctrl <- subset(res_HW1_anti.heat_heat, padj<0.01)
ressig_HW1_anti.heat_ctrl_up <- subset(res_HW1_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti.heat_ctrl_dn <- subset(res_HW1_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl[order(ressig_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_up[order(ressig_HW1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_dn[order(ressig_HW1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti.heat_heat_dn.csv")
colnames(res_HW1_anti.heat_heat)
summary(res_HW1_anti.heat_heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW1_anti.heat_heat.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW1_anti.heat_heat_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW1_anti.heat_heat_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW1_anti.heat_heat_dn_ID.txt-e
```

### Houwan2
#### Antibiotics vs. Control
```{r}
res_HW2_anti_ctrl <- results(dds_HW2, contrast = c("Treatment", "Antibiotics", "control"))
res_HW2_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW2_anti_ctrl$IDGeneInfo <- as.character(res_HW2_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti_ctrl[order(res_HW2_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW2_anti_ctrl.csv")
ressig_HW2_anti_ctrl <- subset(res_HW2_anti_ctrl, padj<0.01)
ressig_HW2_anti_ctrl_up <- subset(res_HW2_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti_ctrl_dn <- subset(res_HW2_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti_ctrl[order(ressig_HW2_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti_ctrl.csv")
write.csv(as.data.frame(ressig_HW2_anti_ctrl_up[order(ressig_HW2_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW2_anti_ctrl_dn[order(ressig_HW2_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti_ctrl_dn.csv")
colnames(res_HW2_anti_ctrl)
summary(res_HW2_anti_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti_ctrl_dn_ID.txt-e
```
#### Heat vs. Control
```{r}
res_HW2_heat_ctrl <- results(dds_HW2, contrast = c("Treatment", "Heat", "control"))
res_HW2_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW2_heat_ctrl$IDGeneInfo <- as.character(res_HW2_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_heat_ctrl[order(res_HW2_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW2_heat_ctrl.csv")
ressig_HW2_heat_ctrl <- subset(res_HW2_heat_ctrl, padj<0.01)
ressig_HW2_heat_ctrl_up <- subset(res_HW2_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW2_heat_ctrl_dn <- subset(res_HW2_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_heat_ctrl[order(ressig_HW2_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW2_heat_ctrl_up[order(ressig_HW2_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW2_heat_ctrl_dn[order(ressig_HW2_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_heat_ctrl_dn.csv")
colnames(res_HW2_heat_ctrl)
summary(res_HW2_heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Control
```{r}
res_HW2_anti.heat_ctrl <- results(dds_HW2, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_HW2_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW2_anti.heat_ctrl$IDGeneInfo <- as.character(res_HW2_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti.heat_ctrl[order(res_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW2_anti.heat_ctrl.csv")
ressig_HW2_anti.heat_ctrl <- subset(res_HW2_anti.heat_ctrl, padj<0.01)
ressig_HW2_anti.heat_ctrl_up <- subset(res_HW2_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti.heat_ctrl_dn <- subset(res_HW2_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl[order(ressig_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_up[order(ressig_HW2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_dn[order(ressig_HW2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti.heat_ctrl_dn.csv")
colnames(res_HW2_anti.heat_ctrl)
summary(res_HW2_anti.heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti.heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti.heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti.heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Antibiotics
```{r}
res_HW2_anti.heat_anti <- results(dds_HW2, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_HW2_anti.heat_anti$IDGeneInfo <- mcols(dds_HW2)$IDGeneInfo
res_HW2_anti.heat_anti$IDGeneInfo <- as.character(res_HW2_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti.heat_anti[order(res_HW2_anti.heat_anti$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW2_anti.heat_anti.csv")
ressig_HW2_anti.heat_ctrl <- subset(res_HW2_anti.heat_anti, padj<0.01)
ressig_HW2_anti.heat_ctrl_up <- subset(res_HW2_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti.heat_ctrl_dn <- subset(res_HW2_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl[order(ressig_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_up[order(ressig_HW2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_dn[order(ressig_HW2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti.heat_anti_dn.csv")
colnames(res_HW2_anti.heat_anti)
summary(res_HW2_anti.heat_anti)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti.heat_anti.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti.heat_anti_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti.heat_anti_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_anti_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Heat
```{r}
res_HW2_anti.heat_heat <- results(dds_HW2, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_HW2_anti.heat_heat$IDGeneInfo <- mcols(dds_HW2)$IDGeneInfo
res_HW2_anti.heat_heat$IDGeneInfo <- as.character(res_HW2_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti.heat_heat[order(res_HW2_anti.heat_heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_HW2_anti.heat_heat.csv")
ressig_HW2_anti.heat_ctrl <- subset(res_HW2_anti.heat_heat, padj<0.01)
ressig_HW2_anti.heat_ctrl_up <- subset(res_HW2_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti.heat_ctrl_dn <- subset(res_HW2_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl[order(ressig_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_up[order(ressig_HW2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_dn[order(ressig_HW2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti.heat_heat_dn.csv")
colnames(res_HW2_anti.heat_heat)
summary(res_HW2_anti.heat_heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_HW2_anti.heat_heat.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_HW2_anti.heat_heat_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_HW2_anti.heat_heat_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_HW2_anti.heat_heat_dn_ID.txt-e
```

### Wanglitung1
#### Antibiotics vs. Control
```{r}
res_WT1_anti_ctrl <- results(dds_WT1, contrast = c("Treatment", "Antibiotics", "control"))
res_WT1_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT1_anti_ctrl$IDGeneInfo <- as.character(res_WT1_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti_ctrl[order(res_WT1_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT1_anti_ctrl.csv")
ressig_WT1_anti_ctrl <- subset(res_WT1_anti_ctrl, padj<0.01)
ressig_WT1_anti_ctrl_up <- subset(res_WT1_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti_ctrl_dn <- subset(res_WT1_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti_ctrl[order(ressig_WT1_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti_ctrl.csv")
write.csv(as.data.frame(ressig_WT1_anti_ctrl_up[order(ressig_WT1_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT1_anti_ctrl_dn[order(ressig_WT1_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti_ctrl_dn.csv")
colnames(res_WT1_anti_ctrl)
summary(res_WT1_anti_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti_ctrl_dn_ID.txt-e
```
#### Heat vs. Control
```{r}
res_WT1_heat_ctrl <- results(dds_WT1, contrast = c("Treatment", "Heat", "control"))
res_WT1_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT1_heat_ctrl$IDGeneInfo <- as.character(res_WT1_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_heat_ctrl[order(res_WT1_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT1_heat_ctrl.csv")
ressig_WT1_heat_ctrl <- subset(res_WT1_heat_ctrl, padj<0.01)
ressig_WT1_heat_ctrl_up <- subset(res_WT1_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT1_heat_ctrl_dn <- subset(res_WT1_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_heat_ctrl[order(ressig_WT1_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT1_heat_ctrl_up[order(ressig_WT1_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT1_heat_ctrl_dn[order(ressig_WT1_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_heat_ctrl_dn.csv")
colnames(res_WT1_heat_ctrl)
summary(res_WT1_heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Control
```{r}
res_WT1_anti.heat_ctrl <- results(dds_WT1, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_WT1_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT1_anti.heat_ctrl$IDGeneInfo <- as.character(res_WT1_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti.heat_ctrl[order(res_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT1_anti.heat_ctrl.csv")
ressig_WT1_anti.heat_ctrl <- subset(res_WT1_anti.heat_ctrl, padj<0.01)
ressig_WT1_anti.heat_ctrl_up <- subset(res_WT1_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti.heat_ctrl_dn <- subset(res_WT1_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl[order(ressig_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_up[order(ressig_WT1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_dn[order(ressig_WT1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti.heat_ctrl_dn.csv")
colnames(res_WT1_anti.heat_ctrl)
summary(res_WT1_anti.heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti.heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti.heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti.heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Antibiotics
```{r}
res_WT1_anti.heat_anti <- results(dds_WT1, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_WT1_anti.heat_anti$IDGeneInfo <- mcols(dds_WT1)$IDGeneInfo
res_WT1_anti.heat_anti$IDGeneInfo <- as.character(res_WT1_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti.heat_anti[order(res_WT1_anti.heat_anti$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT1_anti.heat_anti.csv")
ressig_WT1_anti.heat_ctrl <- subset(res_WT1_anti.heat_anti, padj<0.01)
ressig_WT1_anti.heat_ctrl_up <- subset(res_WT1_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti.heat_ctrl_dn <- subset(res_WT1_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl[order(ressig_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_up[order(ressig_WT1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_dn[order(ressig_WT1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti.heat_anti_dn.csv")
colnames(res_WT1_anti.heat_anti)
summary(res_WT1_anti.heat_anti)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti.heat_anti.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti.heat_anti_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti.heat_anti_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_anti_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Heat
```{r}
res_WT1_anti.heat_heat <- results(dds_WT1, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_WT1_anti.heat_heat$IDGeneInfo <- mcols(dds_WT1)$IDGeneInfo
res_WT1_anti.heat_heat$IDGeneInfo <- as.character(res_WT1_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti.heat_heat[order(res_WT1_anti.heat_heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT1_anti.heat_heat.csv")
ressig_WT1_anti.heat_ctrl <- subset(res_WT1_anti.heat_heat, padj<0.01)
ressig_WT1_anti.heat_ctrl_up <- subset(res_WT1_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti.heat_ctrl_dn <- subset(res_WT1_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl[order(ressig_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_up[order(ressig_WT1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_dn[order(ressig_WT1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti.heat_heat_dn.csv")
colnames(res_WT1_anti.heat_heat)
summary(res_WT1_anti.heat_heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT1_anti.heat_heat.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT1_anti.heat_heat_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT1_anti.heat_heat_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT1_anti.heat_heat_dn_ID.txt-e
```

### Wanglitung2
#### Antibiotics vs. Control
```{r}
res_WT2_anti_ctrl <- results(dds_WT2, contrast = c("Treatment", "Antibiotics", "control"))
res_WT2_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT2_anti_ctrl$IDGeneInfo <- as.character(res_WT2_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti_ctrl[order(res_WT2_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT2_anti_ctrl.csv")
ressig_WT2_anti_ctrl <- subset(res_WT2_anti_ctrl, padj<0.01)
ressig_WT2_anti_ctrl_up <- subset(res_WT2_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti_ctrl_dn <- subset(res_WT2_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti_ctrl[order(ressig_WT2_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti_ctrl.csv")
write.csv(as.data.frame(ressig_WT2_anti_ctrl_up[order(ressig_WT2_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT2_anti_ctrl_dn[order(ressig_WT2_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti_ctrl_dn.csv")
colnames(res_WT2_anti_ctrl)
summary(res_WT2_anti_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti_ctrl_dn_ID.txt-e
```
#### Heat vs. Control
```{r}
res_WT2_heat_ctrl <- results(dds_WT2, contrast = c("Treatment", "Heat", "control"))
res_WT2_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT2_heat_ctrl$IDGeneInfo <- as.character(res_WT2_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_heat_ctrl[order(res_WT2_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT2_heat_ctrl.csv")
ressig_WT2_heat_ctrl <- subset(res_WT2_heat_ctrl, padj<0.01)
ressig_WT2_heat_ctrl_up <- subset(res_WT2_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT2_heat_ctrl_dn <- subset(res_WT2_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_heat_ctrl[order(ressig_WT2_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT2_heat_ctrl_up[order(ressig_WT2_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT2_heat_ctrl_dn[order(ressig_WT2_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_heat_ctrl_dn.csv")
colnames(res_WT2_heat_ctrl)
summary(res_WT2_heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Control
```{r}
res_WT2_anti.heat_ctrl <- results(dds_WT2, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_WT2_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT2_anti.heat_ctrl$IDGeneInfo <- as.character(res_WT2_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti.heat_ctrl[order(res_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT2_anti.heat_ctrl.csv")
ressig_WT2_anti.heat_ctrl <- subset(res_WT2_anti.heat_ctrl, padj<0.01)
ressig_WT2_anti.heat_ctrl_up <- subset(res_WT2_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti.heat_ctrl_dn <- subset(res_WT2_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl[order(ressig_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_up[order(ressig_WT2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_dn[order(ressig_WT2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti.heat_ctrl_dn.csv")
colnames(res_WT2_anti.heat_ctrl)
summary(res_WT2_anti.heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti.heat_ctrl.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti.heat_ctrl_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti.heat_ctrl_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_ctrl_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Antibiotics
```{r}
res_WT2_anti.heat_anti <- results(dds_WT2, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_WT2_anti.heat_anti$IDGeneInfo <- mcols(dds_WT2)$IDGeneInfo
res_WT2_anti.heat_anti$IDGeneInfo <- as.character(res_WT2_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti.heat_anti[order(res_WT2_anti.heat_anti$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT2_anti.heat_anti.csv")
ressig_WT2_anti.heat_ctrl <- subset(res_WT2_anti.heat_anti, padj<0.01)
ressig_WT2_anti.heat_ctrl_up <- subset(res_WT2_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti.heat_ctrl_dn <- subset(res_WT2_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl[order(ressig_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_up[order(ressig_WT2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_dn[order(ressig_WT2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti.heat_anti_dn.csv")
colnames(res_WT2_anti.heat_anti)
summary(res_WT2_anti.heat_anti)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti.heat_anti.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti.heat_anti_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti.heat_anti_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_anti_dn_ID.txt-e
```
#### Antibiotics.Heat vs. Heat
```{r}
res_WT2_anti.heat_heat <- results(dds_WT2, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_WT2_anti.heat_heat$IDGeneInfo <- mcols(dds_WT2)$IDGeneInfo
res_WT2_anti.heat_heat$IDGeneInfo <- as.character(res_WT2_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti.heat_heat[order(res_WT2_anti.heat_heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/all/res_WT2_anti.heat_heat.csv")
ressig_WT2_anti.heat_ctrl <- subset(res_WT2_anti.heat_heat, padj<0.01)
ressig_WT2_anti.heat_ctrl_up <- subset(res_WT2_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti.heat_ctrl_dn <- subset(res_WT2_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl[order(ressig_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_up[order(ressig_WT2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_dn[order(ressig_WT2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti.heat_heat_dn.csv")
colnames(res_WT2_anti.heat_heat)
summary(res_WT2_anti.heat_heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/overall/res_WT2_anti.heat_heat.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/up/res_WT2_anti.heat_heat_up.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_up_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/tables/down/res_WT2_anti.heat_heat_dn.csv > ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_dn_ID.txt
rm ~/computing/scripts/EAPSI_AntiXHeat-master/DESeqresults_Pdam/lists/res_WT2_anti.heat_heat_dn_ID.txt-e
```



# Overall and genotype-specific combined results table
```{r}
genodf <- data.frame(cbind(res_LPS$log2FoldChange, -log10(res_LPS$padj),
                           res_HW1$log2FoldChange, -log10(res_HW1$padj),
                           res_HW2$log2FoldChange, -log10(res_HW2$padj),
                           res_WT1$log2FoldChange, -log10(res_WT1$padj),
                           res_WT2$log2FoldChange, -log10(res_WT2$padj)))
                             #res_anti_ctrl$log2FoldChange, -log10(res_anti_ctrl$padj),
                             #res_heat_ctrl$log2FoldChange, -log10(res_heat_ctrl$padj),
                             #res_anti.heat_ctrl$log2FoldChange, -log10(res_anti.heat_ctrl$padj),
                             #res_anti.heat.LPS_ctrl$log2FoldChange, -log10(res_anti.heat.LPS_ctrl$padj)))
colnames(genodf) <- c("LFC_overall", "padj_overall",
                        "LFC_HW1", "padj_HW1",
                        "LFC_HW2", "padj_HW2",
                        "LFC_WT1", "padj_WT1",
                        "LFC_WT2", "padj_WT2")
genodf$ID <- rownames(genefeatures) 
genodf <- genodf[,c(11, 1:10)]
genodf$IDGeneInfo <- genefeatures$IDGeneInfo

```
```{r}
dpg <- ggplot(genodf[genodf$IDGeneInfo %in% HW12_WT12, ], aes(LFC_overall, LFC_HW2))
dpg + 
  geom_hline(yintercept = 0, color = "black", size = 0.2) +
  geom_vline(xintercept = 0, color = "black", size = 0.2) +
  geom_abline(intercept = 0, slope = 1, color = "black", size = 0.2, linetype = "dashed") +
  scale_x_continuous(limits = c(-3,3), breaks = seq(-3,3,1)) + 
  scale_y_continuous(limits = c(-3,3), breaks = seq(-3,3,1)) +
  geom_point() +
  coord_fixed(1)

#+ 
#  geom_point(aes(color=cDEG_LPS.Anti)) +
#  scale_colour_manual(values = DEGcolors) +
#  geom_text_repel(data = doubledf[doubledf$cDEG_LPS.Anti=="UP_UP",], aes(label = doubledf$IDGeneInfo[doubledf$cDEG_LPS.Anti=="UP_UP"]), size = 1.5, box.padding = unit(0.25, "lines")) +
#  geom_text_repel(data = doubledf[doubledf$cDEG_LPS.Anti=="DN_DN",], aes(label = doubledf$IDGeneInfo[doubledf$cDEG_LPS.Anti=="DN_DN"]), size = 1.5, box.padding = unit(0.25, "lines"))
```
```{r}
consdf <- genodf[genodf$IDGeneInfo %in% HW12_WT12, ]
```


