---
title: "AXH_DESeq-contrasts_Pdam"
author: "Mike Connelly"
date: "12/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/computing/projects/EAPSI_Pocillopora_AxH/")
library(DESeq2)
library(VennDiagram)
```
```{r}
resultsNames(dds_anti)
resultsNames(dds_heat)
resultsNames(dds_anti.heat)
resultsNames(dds_antixheat)
```

##Overall model results contrasts between individual treatments and control samples

### Antibiotics vs. Control
```{r}
res_anti_ctrl <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics", "control"))
res_anti_ctrl$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti_ctrl$IDGeneInfo <- as.character(res_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_anti_ctrl[order(res_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_anti_ctrl.csv")
ressig_anti_ctrl <- subset(res_anti_ctrl, padj<0.01)
ressig_anti_ctrl_up <- subset(res_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_anti_ctrl_dn <- subset(res_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti_ctrl[order(ressig_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_anti_ctrl.csv")
write.csv(as.data.frame(ressig_anti_ctrl_up[order(ressig_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti_ctrl_dn[order(ressig_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_anti_ctrl_dn.csv")
colnames(res_anti_ctrl)
summary(res_anti_ctrl)
```

### Heat vs. Control
```{r}
res_heat_ctrl <- results(dds_antixheat, contrast = c("Treatment", "Heat", "control"))
res_heat_ctrl$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_heat_ctrl$IDGeneInfo <- as.character(res_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_heat_ctrl[order(res_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_heat_ctrl.csv")
ressig_heat_ctrl <- subset(res_heat_ctrl, padj<0.01)
ressig_heat_ctrl_up <- subset(res_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_heat_ctrl_dn <- subset(res_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_heat_ctrl[order(ressig_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_heat_ctrl.csv")
write.csv(as.data.frame(ressig_heat_ctrl_up[order(ressig_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_heat_ctrl_dn[order(ressig_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_heat_ctrl_dn.csv")
colnames(res_heat_ctrl)
summary(res_heat_ctrl)
```

### Antibiotics.Heat vs. Control
```{r}
res_anti.heat_ctrl <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_anti.heat_ctrl$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti.heat_ctrl$IDGeneInfo <- as.character(res_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_anti.heat_ctrl[order(res_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_anti.heat_ctrl.csv")
ressig_anti.heat_ctrl <- subset(res_anti.heat_ctrl, padj<0.01)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_anti.heat_ctrl_dn.csv")
colnames(res_anti.heat_ctrl)
summary(res_anti.heat_ctrl)
```

### Antibiotics.Heat vs. Antibiotics
```{r}
res_anti.heat_anti <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_anti.heat_anti$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti.heat_anti$IDGeneInfo <- as.character(res_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_anti.heat_anti[order(res_anti.heat_anti$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_anti.heat_anti.csv")
ressig_anti.heat_ctrl <- subset(res_anti.heat_anti, padj<0.01)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_anti.heat_anti_dn.csv")
colnames(res_anti.heat_anti)
summary(res_anti.heat_anti)
```

### Antibiotics.Heat vs. Heat
```{r}
res_anti.heat_heat <- results(dds_antixheat, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_anti.heat_heat$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_anti.heat_heat$IDGeneInfo <- as.character(res_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_anti.heat_heat[order(res_anti.heat_heat$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_anti.heat_heat.csv")
ressig_anti.heat_ctrl <- subset(res_anti.heat_heat, padj<0.01)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_anti.heat_heat_dn.csv")
colnames(res_anti.heat_heat)
summary(res_anti.heat_heat)
```

## Results contrasts between different coral genotypes

### Houwan1 vs. Houwan2
```{r}
res_HW1_HW2 <- results(dds_antixheat, contrast = c("Colony", "HW1", "HW2"))
res_HW1_HW2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW1_HW2$IDGeneInfo <- as.character(res_HW1_HW2$IDGeneInfo)
write.csv(as.data.frame(res_HW1_HW2[order(res_HW1_HW2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_HW2.csv")
ressig_HW1_HW2 <- subset(res_HW1_HW2, padj<0.01)
ressig_HW1_HW2_up <- subset(res_HW1_HW2, padj<0.01 & log2FoldChange>0)
ressig_HW1_HW2_dn <- subset(res_HW1_HW2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_HW2[order(ressig_HW1_HW2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_HW2.csv")
write.csv(as.data.frame(ressig_HW1_HW2_up[order(ressig_HW1_HW2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_HW2_up.csv")
write.csv(as.data.frame(ressig_HW1_HW2_dn[order(ressig_HW1_HW2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_HW2_dn.csv")
colnames(res_HW1_HW2)
summary(res_HW1_HW2)
```

### Houwan1 vs. Wanglitung1
```{r}
res_HW1_WT1 <- results(dds_antixheat, contrast = c("Colony", "HW1", "WT1"))
res_HW1_WT1$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW1_WT1$IDGeneInfo <- as.character(res_HW1_WT1$IDGeneInfo)
write.csv(as.data.frame(res_HW1_WT1[order(res_HW1_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_WT1.csv")
ressig_HW1_WT1 <- subset(res_HW1_WT1, padj<0.01)
ressig_HW1_WT1_up <- subset(res_HW1_WT1, padj<0.01 & log2FoldChange>0)
ressig_HW1_WT1_dn <- subset(res_HW1_WT1, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_WT1[order(ressig_HW1_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_WT1.csv")
write.csv(as.data.frame(ressig_HW1_WT1_up[order(ressig_HW1_WT1_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_WT1_up.csv")
write.csv(as.data.frame(ressig_HW1_WT1_dn[order(ressig_HW1_WT1_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_WT1_dn.csv")
colnames(res_HW1_WT1)
summary(res_HW1_WT1)
```

### Houwan1 vs. Wanglitung2
```{r}
res_HW1_WT2 <- results(dds_antixheat, contrast = c("Colony", "HW1", "WT2"))
res_HW1_WT2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW1_WT2$IDGeneInfo <- as.character(res_HW1_WT2$IDGeneInfo)
write.csv(as.data.frame(res_HW1_WT2[order(res_HW1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_WT2.csv")
ressig_HW1_WT2 <- subset(res_HW1_WT2, padj<0.01)
ressig_HW1_WT2_up <- subset(res_HW1_WT2, padj<0.01 & log2FoldChange>0)
ressig_HW1_WT2_dn <- subset(res_HW1_WT2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_WT2[order(ressig_HW1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_WT2.csv")
write.csv(as.data.frame(ressig_HW1_WT2_up[order(ressig_HW1_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_WT2_up.csv")
write.csv(as.data.frame(ressig_HW1_WT2_dn[order(ressig_HW1_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_WT2_dn.csv")
colnames(res_HW1_WT2)
summary(res_HW1_WT2)
```

### Houwan2 vs. Wanglitung1
```{r}
res_HW2_WT1 <- results(dds_antixheat, contrast = c("Colony", "HW2", "WT1"))
res_HW2_WT1$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW2_WT1$IDGeneInfo <- as.character(res_HW2_WT1$IDGeneInfo)
write.csv(as.data.frame(res_HW2_WT1[order(res_HW2_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_WT1.csv")
ressig_HW2_WT1 <- subset(res_HW2_WT1, padj<0.01)
ressig_HW2_WT1_up <- subset(res_HW2_WT1, padj<0.01 & log2FoldChange>0)
ressig_HW2_WT1_dn <- subset(res_HW2_WT1, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_WT1[order(ressig_HW2_WT1$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_WT1.csv")
write.csv(as.data.frame(ressig_HW2_WT1_up[order(ressig_HW2_WT1_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_WT1_up.csv")
write.csv(as.data.frame(ressig_HW2_WT1_dn[order(ressig_HW2_WT1_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_WT1_dn.csv")
colnames(res_HW2_WT1)
summary(res_HW2_WT1)
```

### Houwan2 vs. Wanglitung2
```{r}
res_HW2_WT2 <- results(dds_antixheat, contrast = c("Colony", "HW2", "WT2"))
res_HW2_WT2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_HW2_WT2$IDGeneInfo <- as.character(res_HW2_WT2$IDGeneInfo)
write.csv(as.data.frame(res_HW2_WT2[order(res_HW2_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_WT2.csv")
ressig_HW2_WT2 <- subset(res_HW2_WT2, padj<0.01)
ressig_HW2_WT2_up <- subset(res_HW2_WT2, padj<0.01 & log2FoldChange>0)
ressig_HW2_WT2_dn <- subset(res_HW2_WT2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_WT2[order(ressig_HW2_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_WT2.csv")
write.csv(as.data.frame(ressig_HW2_WT2_up[order(ressig_HW2_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_WT2_up.csv")
write.csv(as.data.frame(ressig_HW2_WT2_dn[order(ressig_HW2_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_WT2_dn.csv")
colnames(res_HW2_WT2)
summary(res_HW2_WT2)
```

### Wanglitung1 vs. Wanglitung2
```{r}
res_WT1_WT2 <- results(dds_antixheat, contrast = c("Colony", "WT1", "WT2"))
res_WT1_WT2$IDGeneInfo <- mcols(dds_antixheat)$IDGeneInfo
res_WT1_WT2$IDGeneInfo <- as.character(res_WT1_WT2$IDGeneInfo)
write.csv(as.data.frame(res_WT1_WT2[order(res_WT1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_WT2.csv")
ressig_WT1_WT2 <- subset(res_WT1_WT2, padj<0.01)
ressig_WT1_WT2_up <- subset(res_WT1_WT2, padj<0.01 & log2FoldChange>0)
ressig_WT1_WT2_dn <- subset(res_WT1_WT2, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_WT2[order(ressig_WT1_WT2$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_WT2.csv")
write.csv(as.data.frame(ressig_WT1_WT2_up[order(ressig_WT1_WT2_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_WT2_up.csv")
write.csv(as.data.frame(ressig_WT1_WT2_dn[order(ressig_WT1_WT2_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_WT2_dn.csv")
colnames(res_WT1_WT2)
summary(res_WT1_WT2)
```

## Colony-specific treatment contrasts results
### Houwan1
#### Antibiotics vs. Control
```{r}
res_HW1_anti_ctrl <- results(dds_HW1, contrast = c("Treatment", "Antibiotics", "control"))
res_HW1_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti_ctrl$IDGeneInfo <- as.character(res_HW1_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti_ctrl[order(res_HW1_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_anti_ctrl.csv")
ressig_HW1_anti_ctrl <- subset(res_HW1_anti_ctrl, padj<0.01)
ressig_HW1_anti_ctrl_up <- subset(res_HW1_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti_ctrl_dn <- subset(res_HW1_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti_ctrl[order(ressig_HW1_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_anti_ctrl.csv")
write.csv(as.data.frame(ressig_HW1_anti_ctrl_up[order(ressig_HW1_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW1_anti_ctrl_dn[order(ressig_HW1_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_anti_ctrl_dn.csv")
colnames(res_HW1_anti_ctrl)
summary(res_HW1_anti_ctrl)
```

#### Heat vs. Control
```{r}
res_HW1_heat_ctrl <- results(dds_HW1, contrast = c("Treatment", "Heat", "control"))
res_HW1_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_heat_ctrl$IDGeneInfo <- as.character(res_HW1_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_heat_ctrl[order(res_HW1_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_heat_ctrl.csv")
ressig_HW1_heat_ctrl <- subset(res_HW1_heat_ctrl, padj<0.01)
ressig_HW1_heat_ctrl_up <- subset(res_HW1_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW1_heat_ctrl_dn <- subset(res_HW1_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_heat_ctrl[order(ressig_HW1_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW1_heat_ctrl_up[order(ressig_HW1_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW1_heat_ctrl_dn[order(ressig_HW1_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_heat_ctrl_dn.csv")
colnames(res_HW1_heat_ctrl)
summary(res_HW1_heat_ctrl)
```

#### Antibiotics.Heat vs. Control
```{r}
res_HW1_anti.heat_ctrl <- results(dds_HW1, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_HW1_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti.heat_ctrl$IDGeneInfo <- as.character(res_HW1_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti.heat_ctrl[order(res_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_anti.heat_ctrl.csv")
ressig_HW1_anti.heat_ctrl <- subset(res_HW1_anti.heat_ctrl, padj<0.01)
ressig_HW1_anti.heat_ctrl_up <- subset(res_HW1_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti.heat_ctrl_dn <- subset(res_HW1_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl[order(ressig_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_up[order(ressig_HW1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_dn[order(ressig_HW1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_anti.heat_ctrl_dn.csv")
colnames(res_HW1_anti.heat_ctrl)
summary(res_HW1_anti.heat_ctrl)
```

#### Antibiotics.Heat vs. Antibiotics
```{r}
res_HW1_anti.heat_anti <- results(dds_HW1, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_HW1_anti.heat_anti$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti.heat_anti$IDGeneInfo <- as.character(res_HW1_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti.heat_anti[order(res_HW1_anti.heat_anti$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_anti.heat_anti.csv")
ressig_HW1_anti.heat_ctrl <- subset(res_HW1_anti.heat_anti, padj<0.01)
ressig_HW1_anti.heat_ctrl_up <- subset(res_HW1_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti.heat_ctrl_dn <- subset(res_HW1_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl[order(ressig_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_up[order(ressig_HW1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_dn[order(ressig_HW1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_anti.heat_anti_dn.csv")
colnames(res_HW1_anti.heat_anti)
summary(res_HW1_anti.heat_anti)
```

#### Antibiotics.Heat vs. Heat
```{r}
res_HW1_anti.heat_heat <- results(dds_HW1, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_HW1_anti.heat_heat$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW1_anti.heat_heat$IDGeneInfo <- as.character(res_HW1_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_HW1_anti.heat_heat[order(res_HW1_anti.heat_heat$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW1_anti.heat_heat.csv")
ressig_HW1_anti.heat_ctrl <- subset(res_HW1_anti.heat_heat, padj<0.01)
ressig_HW1_anti.heat_ctrl_up <- subset(res_HW1_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_HW1_anti.heat_ctrl_dn <- subset(res_HW1_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl[order(ressig_HW1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW1_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_up[order(ressig_HW1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW1_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_HW1_anti.heat_ctrl_dn[order(ressig_HW1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW1_anti.heat_heat_dn.csv")
colnames(res_HW1_anti.heat_heat)
summary(res_HW1_anti.heat_heat)
```

### Houwan2
#### Antibiotics vs. Control
```{r}
res_HW2_anti_ctrl <- results(dds_HW2, contrast = c("Treatment", "Antibiotics", "control"))
res_HW2_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW2_anti_ctrl$IDGeneInfo <- as.character(res_HW2_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti_ctrl[order(res_HW2_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_anti_ctrl.csv")
ressig_HW2_anti_ctrl <- subset(res_HW2_anti_ctrl, padj<0.01)
ressig_HW2_anti_ctrl_up <- subset(res_HW2_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti_ctrl_dn <- subset(res_HW2_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti_ctrl[order(ressig_HW2_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_anti_ctrl.csv")
write.csv(as.data.frame(ressig_HW2_anti_ctrl_up[order(ressig_HW2_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW2_anti_ctrl_dn[order(ressig_HW2_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_anti_ctrl_dn.csv")
colnames(res_HW2_anti_ctrl)
summary(res_HW2_anti_ctrl)
```

#### Heat vs. Control
```{r}
res_HW2_heat_ctrl <- results(dds_HW2, contrast = c("Treatment", "Heat", "control"))
res_HW2_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW2_heat_ctrl$IDGeneInfo <- as.character(res_HW2_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_heat_ctrl[order(res_HW2_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_heat_ctrl.csv")
ressig_HW2_heat_ctrl <- subset(res_HW2_heat_ctrl, padj<0.01)
ressig_HW2_heat_ctrl_up <- subset(res_HW2_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW2_heat_ctrl_dn <- subset(res_HW2_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_heat_ctrl[order(ressig_HW2_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW2_heat_ctrl_up[order(ressig_HW2_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW2_heat_ctrl_dn[order(ressig_HW2_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_heat_ctrl_dn.csv")
colnames(res_HW2_heat_ctrl)
summary(res_HW2_heat_ctrl)
```

#### Antibiotics.Heat vs. Control
```{r}
res_HW2_anti.heat_ctrl <- results(dds_HW2, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_HW2_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_HW2_anti.heat_ctrl$IDGeneInfo <- as.character(res_HW2_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti.heat_ctrl[order(res_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_anti.heat_ctrl.csv")
ressig_HW2_anti.heat_ctrl <- subset(res_HW2_anti.heat_ctrl, padj<0.01)
ressig_HW2_anti.heat_ctrl_up <- subset(res_HW2_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti.heat_ctrl_dn <- subset(res_HW2_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl[order(ressig_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_up[order(ressig_HW2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_dn[order(ressig_HW2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_anti.heat_ctrl_dn.csv")
colnames(res_HW2_anti.heat_ctrl)
summary(res_HW2_anti.heat_ctrl)
```

#### Antibiotics.Heat vs. Antibiotics
```{r}
res_HW2_anti.heat_anti <- results(dds_HW2, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_HW2_anti.heat_anti$IDGeneInfo <- mcols(dds_HW2)$IDGeneInfo
res_HW2_anti.heat_anti$IDGeneInfo <- as.character(res_HW2_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti.heat_anti[order(res_HW2_anti.heat_anti$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_anti.heat_anti.csv")
ressig_HW2_anti.heat_ctrl <- subset(res_HW2_anti.heat_anti, padj<0.01)
ressig_HW2_anti.heat_ctrl_up <- subset(res_HW2_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti.heat_ctrl_dn <- subset(res_HW2_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl[order(ressig_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_up[order(ressig_HW2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_dn[order(ressig_HW2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_anti.heat_anti_dn.csv")
colnames(res_HW2_anti.heat_anti)
summary(res_HW2_anti.heat_anti)
```

#### Antibiotics.Heat vs. Heat
```{r}
res_HW2_anti.heat_heat <- results(dds_HW2, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_HW2_anti.heat_heat$IDGeneInfo <- mcols(dds_HW2)$IDGeneInfo
res_HW2_anti.heat_heat$IDGeneInfo <- as.character(res_HW2_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_HW2_anti.heat_heat[order(res_HW2_anti.heat_heat$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_HW2_anti.heat_heat.csv")
ressig_HW2_anti.heat_ctrl <- subset(res_HW2_anti.heat_heat, padj<0.01)
ressig_HW2_anti.heat_ctrl_up <- subset(res_HW2_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_HW2_anti.heat_ctrl_dn <- subset(res_HW2_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl[order(ressig_HW2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_HW2_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_up[order(ressig_HW2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_HW2_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_HW2_anti.heat_ctrl_dn[order(ressig_HW2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_HW2_anti.heat_heat_dn.csv")
colnames(res_HW2_anti.heat_heat)
summary(res_HW2_anti.heat_heat)
```

### Wanglitung1
#### Antibiotics vs. Control
```{r}
res_WT1_anti_ctrl <- results(dds_WT1, contrast = c("Treatment", "Antibiotics", "control"))
res_WT1_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT1_anti_ctrl$IDGeneInfo <- as.character(res_WT1_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti_ctrl[order(res_WT1_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_anti_ctrl.csv")
ressig_WT1_anti_ctrl <- subset(res_WT1_anti_ctrl, padj<0.01)
ressig_WT1_anti_ctrl_up <- subset(res_WT1_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti_ctrl_dn <- subset(res_WT1_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti_ctrl[order(ressig_WT1_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_anti_ctrl.csv")
write.csv(as.data.frame(ressig_WT1_anti_ctrl_up[order(ressig_WT1_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT1_anti_ctrl_dn[order(ressig_WT1_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_anti_ctrl_dn.csv")
colnames(res_WT1_anti_ctrl)
summary(res_WT1_anti_ctrl)
```

#### Heat vs. Control
```{r}
res_WT1_heat_ctrl <- results(dds_WT1, contrast = c("Treatment", "Heat", "control"))
res_WT1_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT1_heat_ctrl$IDGeneInfo <- as.character(res_WT1_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_heat_ctrl[order(res_WT1_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_heat_ctrl.csv")
ressig_WT1_heat_ctrl <- subset(res_WT1_heat_ctrl, padj<0.01)
ressig_WT1_heat_ctrl_up <- subset(res_WT1_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT1_heat_ctrl_dn <- subset(res_WT1_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_heat_ctrl[order(ressig_WT1_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT1_heat_ctrl_up[order(ressig_WT1_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT1_heat_ctrl_dn[order(ressig_WT1_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_heat_ctrl_dn.csv")
colnames(res_WT1_heat_ctrl)
summary(res_WT1_heat_ctrl)
```

#### Antibiotics.Heat vs. Control
```{r}
res_WT1_anti.heat_ctrl <- results(dds_WT1, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_WT1_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT1_anti.heat_ctrl$IDGeneInfo <- as.character(res_WT1_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti.heat_ctrl[order(res_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_anti.heat_ctrl.csv")
ressig_WT1_anti.heat_ctrl <- subset(res_WT1_anti.heat_ctrl, padj<0.01)
ressig_WT1_anti.heat_ctrl_up <- subset(res_WT1_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti.heat_ctrl_dn <- subset(res_WT1_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl[order(ressig_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_up[order(ressig_WT1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_dn[order(ressig_WT1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_anti.heat_ctrl_dn.csv")
colnames(res_WT1_anti.heat_ctrl)
summary(res_WT1_anti.heat_ctrl)
```

#### Antibiotics.Heat vs. Antibiotics
```{r}
res_WT1_anti.heat_anti <- results(dds_WT1, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_WT1_anti.heat_anti$IDGeneInfo <- mcols(dds_WT1)$IDGeneInfo
res_WT1_anti.heat_anti$IDGeneInfo <- as.character(res_WT1_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti.heat_anti[order(res_WT1_anti.heat_anti$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_anti.heat_anti.csv")
ressig_WT1_anti.heat_ctrl <- subset(res_WT1_anti.heat_anti, padj<0.01)
ressig_WT1_anti.heat_ctrl_up <- subset(res_WT1_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti.heat_ctrl_dn <- subset(res_WT1_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl[order(ressig_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_up[order(ressig_WT1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_dn[order(ressig_WT1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_anti.heat_anti_dn.csv")
colnames(res_WT1_anti.heat_anti)
summary(res_WT1_anti.heat_anti)
```

#### Antibiotics.Heat vs. Heat
```{r}
res_WT1_anti.heat_heat <- results(dds_WT1, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_WT1_anti.heat_heat$IDGeneInfo <- mcols(dds_WT1)$IDGeneInfo
res_WT1_anti.heat_heat$IDGeneInfo <- as.character(res_WT1_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_WT1_anti.heat_heat[order(res_WT1_anti.heat_heat$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT1_anti.heat_heat.csv")
ressig_WT1_anti.heat_ctrl <- subset(res_WT1_anti.heat_heat, padj<0.01)
ressig_WT1_anti.heat_ctrl_up <- subset(res_WT1_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_WT1_anti.heat_ctrl_dn <- subset(res_WT1_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl[order(ressig_WT1_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT1_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_up[order(ressig_WT1_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT1_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_WT1_anti.heat_ctrl_dn[order(ressig_WT1_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT1_anti.heat_heat_dn.csv")
colnames(res_WT1_anti.heat_heat)
summary(res_WT1_anti.heat_heat)
```

### Wanglitung2
#### Antibiotics vs. Control
```{r}
res_WT2_anti_ctrl <- results(dds_WT2, contrast = c("Treatment", "Antibiotics", "control"))
res_WT2_anti_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT2_anti_ctrl$IDGeneInfo <- as.character(res_WT2_anti_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti_ctrl[order(res_WT2_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT2_anti_ctrl.csv")
ressig_WT2_anti_ctrl <- subset(res_WT2_anti_ctrl, padj<0.01)
ressig_WT2_anti_ctrl_up <- subset(res_WT2_anti_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti_ctrl_dn <- subset(res_WT2_anti_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti_ctrl[order(ressig_WT2_anti_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT2_anti_ctrl.csv")
write.csv(as.data.frame(ressig_WT2_anti_ctrl_up[order(ressig_WT2_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT2_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT2_anti_ctrl_dn[order(ressig_WT2_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT2_anti_ctrl_dn.csv")
colnames(res_WT2_anti_ctrl)
summary(res_WT2_anti_ctrl)
```

#### Heat vs. Control
```{r}
res_WT2_heat_ctrl <- results(dds_WT2, contrast = c("Treatment", "Heat", "control"))
res_WT2_heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT2_heat_ctrl$IDGeneInfo <- as.character(res_WT2_heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_heat_ctrl[order(res_WT2_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT2_heat_ctrl.csv")
ressig_WT2_heat_ctrl <- subset(res_WT2_heat_ctrl, padj<0.01)
ressig_WT2_heat_ctrl_up <- subset(res_WT2_heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT2_heat_ctrl_dn <- subset(res_WT2_heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_heat_ctrl[order(ressig_WT2_heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT2_heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT2_heat_ctrl_up[order(ressig_WT2_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT2_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT2_heat_ctrl_dn[order(ressig_WT2_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT2_heat_ctrl_dn.csv")
colnames(res_WT2_heat_ctrl)
summary(res_WT2_heat_ctrl)
```

#### Antibiotics.Heat vs. Control
```{r}
res_WT2_anti.heat_ctrl <- results(dds_WT2, contrast = c("Treatment", "Antibiotics.Heat", "control"))
res_WT2_anti.heat_ctrl$IDGeneInfo <- mcols(dds_HW1)$IDGeneInfo
res_WT2_anti.heat_ctrl$IDGeneInfo <- as.character(res_WT2_anti.heat_ctrl$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti.heat_ctrl[order(res_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT2_anti.heat_ctrl.csv")
ressig_WT2_anti.heat_ctrl <- subset(res_WT2_anti.heat_ctrl, padj<0.01)
ressig_WT2_anti.heat_ctrl_up <- subset(res_WT2_anti.heat_ctrl, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti.heat_ctrl_dn <- subset(res_WT2_anti.heat_ctrl, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl[order(ressig_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT2_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_up[order(ressig_WT2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT2_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_dn[order(ressig_WT2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT2_anti.heat_ctrl_dn.csv")
colnames(res_WT2_anti.heat_ctrl)
summary(res_WT2_anti.heat_ctrl)
```

#### Antibiotics.Heat vs. Antibiotics
```{r}
res_WT2_anti.heat_anti <- results(dds_WT2, contrast = c("Treatment", "Antibiotics.Heat", "Antibiotics"))
res_WT2_anti.heat_anti$IDGeneInfo <- mcols(dds_WT2)$IDGeneInfo
res_WT2_anti.heat_anti$IDGeneInfo <- as.character(res_WT2_anti.heat_anti$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti.heat_anti[order(res_WT2_anti.heat_anti$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT2_anti.heat_anti.csv")
ressig_WT2_anti.heat_ctrl <- subset(res_WT2_anti.heat_anti, padj<0.01)
ressig_WT2_anti.heat_ctrl_up <- subset(res_WT2_anti.heat_anti, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti.heat_ctrl_dn <- subset(res_WT2_anti.heat_anti, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl[order(ressig_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT2_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_up[order(ressig_WT2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT2_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_dn[order(ressig_WT2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT2_anti.heat_anti_dn.csv")
colnames(res_WT2_anti.heat_anti)
summary(res_WT2_anti.heat_anti)
```

#### Antibiotics.Heat vs. Heat
```{r}
res_WT2_anti.heat_heat <- results(dds_WT2, contrast = c("Treatment", "Antibiotics.Heat", "Heat"))
res_WT2_anti.heat_heat$IDGeneInfo <- mcols(dds_WT2)$IDGeneInfo
res_WT2_anti.heat_heat$IDGeneInfo <- as.character(res_WT2_anti.heat_heat$IDGeneInfo)
###
write.csv(as.data.frame(res_WT2_anti.heat_heat[order(res_WT2_anti.heat_heat$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/all/res_WT2_anti.heat_heat.csv")
ressig_WT2_anti.heat_ctrl <- subset(res_WT2_anti.heat_heat, padj<0.01)
ressig_WT2_anti.heat_ctrl_up <- subset(res_WT2_anti.heat_heat, padj<0.01 & log2FoldChange>0)
ressig_WT2_anti.heat_ctrl_dn <- subset(res_WT2_anti.heat_heat, padj<0.01 & log2FoldChange<0)
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl[order(ressig_WT2_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/overall/res_WT2_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_up[order(ressig_WT2_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "./outputs/DESeq-results/tables/up/res_WT2_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_WT2_anti.heat_ctrl_dn[order(ressig_WT2_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "./outputs/DESeq-results/tables/down/res_WT2_anti.heat_heat_dn.csv")
colnames(res_WT2_anti.heat_heat)
summary(res_WT2_anti.heat_heat)
```

# Overall and genotype-specific combined results table