---
title: "Pocillopora_AXH_microbiome_analysis"
author: "Mike Connelly"
date: "7/28/2020"
output: 
  html_document:
      code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/computing/projects/EAPSI_Pocillopora_AXH")
# some aspects of this microbiome analysis follow: https://github.com/meyermicrobiolab/Stony-Coral-Tissue-Loss-Disease-SCTLD-Project
```
## Setup packages and working directories
```{r packages, include=FALSE}
library("plyr")
library("tidyverse")
# Essential microbiome analysis packages
library("phyloseq")
library("microbiome")
library("zCompositions")
library("CoDaSeq") # devtools::install_github('ggloor/CoDaSeq/CoDaSeq')
library("vegan")
library("ape")
library("ALDEx2")
# Data visualization packages
library("pheatmap")
library("data.table")
library("DT")
# Graphics packages
library("ggbiplot") # library(devtools); install_github("vqv/ggbiplot")
library("ggh4x") # devtools::install_github("teunbrand/ggh4x") 
library("plotrix")
library("cowplot")
library("patchwork")
library("gtable")
library("grid")
library("gridExtra")
library("ggthemes")
library("ggpubr")
library("ggrepel")
library("ggnewscale")
library("RColorBrewer")
library("randomcoloR")
library("wesanderson")
library("circlize")
library("stringr")
library("extrafont")
library("extrafontdb")
# extended visualization functions
source("./R/ggrare.R")
source("./R/AXH_functions.R")
```
```{r colors}
### Set overall theme, colors, and shapes for ggplot2
# remember to set theme_mec() from transcriptomic script for proper formatting
theme_set(theme_mec())
# colors for experimental treatments
condcolors_AxH <- c("blue", "darkorange", "cyan", "gold")
condcolors_heat <- c(condcolors_AxH[1:2])
condcolors_anti <- c(condcolors_AxH[1], condcolors_AxH[3])
condcolors_anti.heat <- c(condcolors_AxH[1], condcolors_AxH[4])
condfillcolors_AxH <- c("#99CCFF", "#FFCC99", "#99FFFF", "#FFFF66") # fill colors for some figures
# shapes and colors for colonies
colshapes <- c(21, 24, 22, 23)
colcolors <- c("olivedrab3", "springgreen", "deepskyblue", "skyblue")
# null colors for presentation figures
condcolors_null <- c(rep("black", 4))
colshapes_null <- c(rep(20, 8))
# color vector for barplot facet strips
cond_col_colors <- c(condfillcolors_AxH[1], colcolors,
                     condfillcolors_AxH[2], colcolors,
                     condfillcolors_AxH[3], colcolors,
                     condfillcolors_AxH[4], colcolors)
```

## Read in ASV table, taxonomy, sample data
```{r asv}
# Read in ASV table
ASV <- read.table("./outputs/qiime2/export_silva/all_silva_feature-table.tsv", row.names = 1, header = TRUE)
ASV <- t(ASV)
```
```{r taxomony}
# Read in taxononomic classification information
taxonomy <- as.matrix(read.table("./outputs/qiime2/export_silva/taxonomy4.txt", sep = "\t", row.names = 1, header = FALSE, fill = TRUE))
colnames(taxonomy) <- c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species")
taxonomy[taxonomy==""] <- NA
taxonomy <- gsub("^D_[0-6]__", "", taxonomy)
taxonomy <- gsub("^Euryarchaeota archaeon SCGC", "", taxonomy) # remove excessively long family name for ease in plotting later
taxa_df <- data.frame(taxonomy) %>% rownames_to_column("ASV")
```
```{r tree_metadata}
# Read in phylogenetic tree, sample metadata and set factor orders
tree <- read_tree("./outputs/qiime2/export_silva/tree.nwk")
map <- read.table("./data/qiime2_metadata.tsv", sep ="\t", row.names = 1, header = FALSE)
colnames(map) <- c ("Reef",	"Colony",	"Environment",	"Treatment")
map$SampleID <- rownames(map)
map$Reef <- factor(map$Reef, levels = c("Houwan", "Wanglitung", "controls"), ordered = TRUE)
map$Colony <- factor(map$Colony, levels = c("HW1", "HW2", "WT1", "WT2", "controls"), ordered = TRUE)
map$Treatment <- factor(map$Treatment, levels = c("control", "Heat", "Antibiotics", "Antibiotics.Heat", "positive", "negative"), ordered = TRUE)
```
## Create phyloseq object
```{r phyloseq}
ps <- phyloseq(otu_table(ASV, taxa_are_rows = FALSE),
               sample_data(map),
               tax_table(taxonomy),
               phy_tree(tree))
ps
# summarize_phyloseq(ps)
```
```{r ps_AxH_all}
# Pre-process, filter, and QC phyloseq object
# Stable site control, Heat, Antibiotics, Antibiotics.Heat sample subset
nsamples(ps)
samples <- sample_names(ps)
# regex to select Hw1, Hw2, Wt1, and Wt2 genotypes in control (6), heat stress (4), antibiotics (5), and combined (1) treatments
samples_AXH <- grep("[HW][wt][1-2].[1456][abc]", samples, value = TRUE) 
ps_AXH_all <- prune_samples(samples_AXH, ps)
ps_AXH_all
# 48 samples, 5 sample variables
```
```{r subset_filter_taxa_samples}
# Retain only assigned taxa
ps_assigned <- subset_taxa(ps, Kingdom != "Unassigned") # 9 unassigned taxa filtered out
ps_assigned <- subset_taxa(ps_assigned, Order != "Chloroplast") # 52 taxa filtered out
ps_assigned <- subset_taxa(ps_assigned, Family != "Mitochondria") # 10 taxa filtered out
ps_assigned
# 470 taxa and 7 taxonomic ranks
# select Hw1, Hw2, Wt1, and Wt2 genotypes in control (6), heat stress (4), antibiotics (5), and combined (1) treatments
ps_assigned_AXH <- prune_samples(samples_AXH, ps_assigned)
# ps_assigned_AXH
# 48 samples
# Filter taxa that have a mean count of 3 across all coral samples
ps_filtered_AXH <- filter_taxa(ps_assigned_AXH, function(x) mean(x) > 3, TRUE) # 60 taxa mean count greater than 1
# or keep unfiltered 
# ps_filtered_AXH <- ps_assigned_AXH
```
```{r inspect_filtered_phyloseq}
ntaxa(ps_filtered_AXH) 
# 
get_taxa_unique(ps_filtered_AXH, "Phylum") %>% length()
get_taxa_unique(ps_filtered_AXH, "Class") %>% length()
get_taxa_unique(ps_filtered_AXH, "Order") %>% length()
get_taxa_unique(ps_filtered_AXH, "Family") %>% length()
get_taxa_unique(ps_filtered_AXH, "Genus") %>% length()
# filtered ASVs with very low abundance with phyloseq, now export otu and taxa tables from phyloseq for codaseq
otu <- as(otu_table(ps_filtered_AXH), "matrix")
taxon <- as(tax_table(ps_filtered_AXH), "matrix")
taxa_df_filtered <- data.frame(taxon) %>% rownames_to_column("ASV")
sample_metadata <- data.frame(sample_data(ps_filtered_AXH))
family <- as.character(taxon[,"Family"])
genus <- as.character(taxon[,"Genus"])
# genus
```
```{r centered_log-ratio_transform}
# Transform zero counts using the count zero multiplicative method in zCompositions, Palarea-Albaladejo and Martín-Fernández, 2015: https://doi.org/10.1016/j.chemolab.2015.02.019
# First, replace 0 values with an estimate (because normalization is taking log, can't have 0)
# Also transpose here, need samples as rows
otu_czm <- cmultRepl(t(otu), method = "CZM", label = 0) # 464 corrected values
# Perform the center-log-ratio (CLR) transformation, recommended by Gloor et al. 2017: https://doi.org/10.3389/fmicb.2017.02224
otu_clr <- codaSeq.clr(otu_czm)
```
## Compositional Data Analysis (CoDA) 
### Beta diversity ordinations
```{r codaseq}
# transpose matrix of CLR transformed data for ordination and dendrogram
e_clr <- t(otu_clr)
# plot compositional PCA biplot (perform a singular value decomposition)
d_pcx <- prcomp(e_clr)
# inspect pca results
summary(d_pcx)
str(d_pcx)
screeplot(d_pcx)
# calculate percent variance explained for the axis labels
pc1 <- round(d_pcx$sdev[1]^2/sum(d_pcx$sdev^2),3)*100
pc2 <- round(d_pcx$sdev[2]^2/sum(d_pcx$sdev^2),3)*100
xlab <- paste("PC1: ", pc1, "%", sep="")
ylab <- paste("PC2: ", pc2, "%", sep="")
```
```{r clr_pca_biplot}
pdf("./outputs/phyloseq-results/figures/CoDA_PCA_biplot.pdf")
biplot(d_pcx, cex=c(0.6,0.4), var.axes=F,scale=1, xlab=xlab, ylab=ylab, ylabs=family)
ggbiplot(d_pcx,
         choices = c(1,2),
         groups = sample_metadata$Treatment,
         varname.abbrev = T) + scale_color_manual(values = condcolors_AxH)
```
```{r clr_ggbiplot}
pca_clr_biplot <- d_pcx %>% 
  gg_biplot(., choices = c(1,2),
            groups = sample_metadata$Treatment,
            groups2 = sample_metadata$Colony,
            ellipse = TRUE,
            taxlabs = "Family",
            varname.abbrev = F,
            varname.size = 1.8) +
  scale_color_manual(values = condcolors_AxH, name = "Treatment") +
  scale_fill_manual(values = condcolors_AxH, name = "Treatment") +
  scale_shape_manual(values = colshapes, name = "Colony") +
  guides(color = guide_legend(override.aes = list(color = condcolors_AxH, alpha = 1, stroke = 1)),
         shape = guide_legend(override.aes = list(shape = colshapes, fill = "black", alpha = 1, stroke = 0.5))) +
  coord_fixed(xlim = c(-2, 2.5), ylim = c(-2.6, 2))

ggsave(pca_clr_biplot, filename = "./outputs/phyloseq-results/figures/clr_ggbiplot.pdf", width = 140, height = 120, units = "mm", device = "pdf")
ggsave(pca_clr_biplot, filename = "./manuscript_figures/Fig3A_CLR_PCA_16S_Treatment.pdf", width = 130, height = 100, units = "mm", device = "pdf")
```
```{r clr_pca}
pcs_clr <- data.frame(d_pcx$x) %>%
  rownames_to_column("SampleID") %>% 
  left_join(sample_metadata, by = "SampleID")
# 
pcs_clr_centroids <- pcs_clr %>% 
  group_by(Treatment) %>% 
  dplyr::summarise(c1 = mean(`PC1`), c2 = mean(`PC2`)) %>% 
  full_join(pcs_clr, by = "Treatment")
# 
pca_clr <- pcs_clr_centroids %>% ggplot(aes(PC1, PC2)) + 
  #sample-centroid spiders paths
    # geom_segment(mapping = aes(x = `PC1`, y = `PC2`, xend = c1, yend = c2), lwd = 0.25, col = "dark grey") +
    #treatment centroid points
    # geom_point(size = 4, aes(x = c1, y = c2, color = Treatment), fill = "black", shape = 21, stroke = 2, show.legend = F) +
    #sample points
    geom_point(size = 3, aes(fill = Treatment, shape = Colony), color = "black", stroke = 0.5, show.legend = FALSE) +
    scale_color_manual(values = condcolors_AxH, name = "Treatment") +
    scale_fill_manual(values = condcolors_AxH, name = "Treatment") +
    scale_shape_manual(values = colshapes, name = "Colony") +
    labs(x=xlab, y=ylab) +
    # guides(shape = guide_legend(override.aes = list(shape = colshapes, alpha = 1, stroke = 0.5))) +
    coord_fixed()
print(pca_clr)
# 
ggsave(pca_clr, filename = "./outputs/phyloseq-results/figures/clr_pca_treatment.pdf", width = 140, height = 100, units = "mm", device = "pdf")
```
```{r clr_taxa_pca}
# Plot coordintaes of the taxa rotations along axes PC1 and PC2
pcs_clr_taxa <- data.frame(d_pcx$rotation) %>% 
  rownames_to_column("ASV") %>% 
  left_join(taxa_df_filtered, by = "ASV")
pca_taxa <- pcs_clr_taxa %>% ggplot(aes(PC1, PC2)) + 
  geom_point(size = 2, color = "black") +
  geom_text_repel(size = 2, aes(label = Genus)) +
  scale_color_manual(values = families_colors$colors) +
  labs(x=xlab, y=ylab) +
  # guides(fill = guide_legend(nrow = 3)) +
  # theme(legend.position = "bottom") +
  coord_fixed()
  print(pca_taxa)
ggsave(pca_taxa, filename = "./outputs/phyloseq-results/figures/clr_pca_taxa.pdf", width = 140, height = 100, units = "mm", device = "pdf")
```



### Beta diversity statistical testing
```{r distance_matrix}
# Calculate Aitchinson distance matrix
dist_clr <- dist(e_clr)
# The Aitchison distance is superior to both the widely used Jensen-Shannon divergence and the Bray-Curtis dissimilarity metrics, being more stable to subsetting and aggregating of the data, and being a true linear distance (Gloor et al. 2017)
# Now obtain data frame from the sample_data
# head(sample_metadata)
# Create factors for statistical testing
treatments <- as.character(sample_metadata$Treatment)
sites <- as.character(sample_metadata$Reef)
colonies <- as.character(sample_metadata$Colony)
```

#### ANOSIM
```{r anosim}
# anosim between groups using Aitchison distance
# Treatment
anosim_treatment <- anosim(dist_clr, treatments, permutations = 999)
plot(anosim_treatment)
# Reef
anosim_site <- anosim(dist_clr, sites, permutations = 999)
plot(anosim_site)
# Colony
anosim_colony <- anosim(dist_clr, colonies, permutations = 999)
plot(anosim_colony)
# All ANOSIM tests for each factor yield significant results
```

#### PERMDISP
```{r permdisp}
# PERMDISP tests
beta_treatment <- betadisper(dist_clr, treatments)
permutest(beta_treatment)
beta_site <- betadisper(dist_clr, sites)
permutest(beta_site)
beta_colony <- betadisper(dist_clr, colonies)
permutest(beta_colony)
# All PERMDISP tests reject hypothesis for homogeneity of multivariate dispersions
```

#### PERMANOVA
```{r permanova}
# Adonis/PERMANOVA tests
# Treatment
permanova_treatment <- adonis(dist_clr ~ treatments, data = sample_metadata)
print(permanova_treatment)
# 
permanova_site <- adonis(dist_clr ~ sites, data = sample_metadata)
print(permanova_site)
# 
permanova_colony <- adonis(dist_clr ~ colonies, data = sample_metadata)
print(permanova_colony)
```

#### Distances to centroids boxplots
```{r betadisper}
# PERMDISP2 procedure for the analysis of multivariate homogeneity of group dispersions (variances).
mod <- betadisper(dist_clr, treatments, type = "centroid")
mod
# 
anova(mod)
# Permutation test for F
permutest(mod, pairwise = TRUE)
(mod.HSD <- TukeyHSD(mod))
# inspect
plot(mod)
boxplot(mod)
```
```{r beta_boxplot}
# Draw a boxplot of the distances to centroid for each group
# first extract the distances to centroids
mod$distance
mod_distance <- data.frame(mod$distance) %>%
  rownames_to_column(., "SampleID") %>%
  left_join(., sample_metadata, by = "SampleID", .keep = TRUE)
# 
beta_boxplot <- mod_distance %>%
  ggplot(aes(Treatment, mod.distance)) + 
  geom_boxplot(aes(fill = Treatment)) +
  scale_fill_manual(values = condfillcolors_AxH) +
  new_scale_fill() + 
  geom_point(aes(color = Treatment, shape = Colony), size = 3, alpha = 0.8) +
  geom_point(size = 3, aes(fill = Treatment, shape = Colony), color = "black", stroke = 0.5, show.legend = FALSE) +
  scale_color_manual(values = condcolors_AxH) +
  scale_fill_manual(values = condcolors_AxH) +
  scale_shape_manual(values = colshapes, name="Colony") + 
  scale_x_discrete(labels = c("C", "H", "A", "A+H")) +
  #ylim(c(0,100)) +
  xlab(NULL) +
  ylab("Beta diversity distance to centroid") +
  # ggtitle("Beta diversity distance to centroid boxplot") +
  theme(legend.position = "none",
          axis.text.x = element_text(angle = 0),
        strip.background = element_blank(),
        strip.text = element_blank())
beta_boxplot
ggsave(beta_boxplot, filename = "./outputs/phyloseq-results/figures/beta_dist-centroid_boxplot.pdf", width = 50, height = 80, units = "mm")
ggsave(beta_boxplot, filename = "./manuscript_figures/Fig3B_beta_dist-centroid_boxplot.pdf", width = 50, height = 80, units = "mm")
```
## Taxa composition plots
```{r relative_abundance_transform}
ps_filtered_AXH_rel <- transform_sample_counts(ps_filtered_AXH, function(x) {x / sum(x)})
ps_filtered_AXH_rel
```

```{r taxa colors, include=FALSE}
# run below taxa colors command until you get a set of colors you like, then comment out and write to csv file for custom edits!

# # Bacteria taxa
# # Phyla
colors_phyla <- taxa_color_seq(ps_filtered_AXH_rel, taxa_rank = "Phylum") 

# # Classes
colors_classes <- taxa_color_seq(ps_filtered_AXH_rel, taxa_rank = "Class") 

# # Orders
colors_orders <- taxa_color_seq(ps_filtered_AXH_rel, taxa_rank = "Order")

# # Families
colors_families <- taxa_color_seq(ps_filtered_AXH_rel, taxa_rank = "Family")

# # Genera
colors_genera <- taxa_color_seq(ps_filtered_AXH_rel, taxa_rank = "Genus")

# # Specices
colors_species <- taxa_color_seq(ps_filtered_AXH_rel, taxa_rank = "Species")

```

### Taxa barplots
```{r taxa_barplots}
taxa_barplot(ps_filtered_AXH_rel, "Phylum", colors_phyla$Phylum, colors_phyla)
taxa_barplot(ps_filtered_AXH_rel, "Class", colors_classes$Class, colors_classes)
taxa_barplot(ps_filtered_AXH_rel, "Order", colors_orders$Order, colors_orders)
taxa_barplot(ps_filtered_AXH_rel, "Family", colors_families$Family, colors_families)
taxa_barplot(ps_filtered_AXH_rel, "Genus", colors_genera$Genus, colors_genera)
```
```{r family_barplot_3B}
pdf("./outputs/phyloseq-results/figures/family_barplot.pdf", height = 3.5, width = 6.5)
taxa_barplot(ps_filtered_AXH_rel, "Family", colors_families$Family, colors_families)
pdf("./manuscript_figures/Fig3C_family_barplot.pdf", height = 3.5, width = 6.5)
taxa_barplot(ps_filtered_AXH_rel, "Family", colors_families$Family, colors_families)
```


## Alpha diversity plots and statistics
```{r estimate_richness}
ps_AXH_richness <- estimate_richness(ps_assigned_AXH) %>% rownames_to_column("SampleID")
alphameasures <- c("Observed", "Chao1", "ACE", "Shannon", "Simpson", "InvSimpson", "Fisher")
```
### Overall alpha diversity boxplots
```{r}
plot_richness(ps_filtered_AXH, x="Treatment", measures = alphameasures) +
  geom_boxplot(aes(fill = Treatment)) +
  scale_fill_manual(values = condfillcolors_AxH) +
  new_scale_fill() + 
  geom_point(aes(color = Treatment, shape = Colony), size = 3, alpha = 0.8) +
  geom_point(size = 3, aes(fill = Treatment, shape = Colony), color = "black", stroke = 0.5, show.legend = FALSE) +
  scale_color_manual(values = condcolors_AxH) +
  scale_fill_manual(values = condcolors_AxH) +
  scale_shape_manual(values = colshapes, name="Colony")
```
```{r}
#pdf(file = "./outputs/phyloseq-results/figures/richness_ctrl.LPS.pdf", height = 2.95, width = 4.5)
plot_richness(ps_filtered_AXH, x="Treatment", measures=c("Chao1", "Simpson", "Shannon")) +
 geom_boxplot(aes(fill = Treatment)) +
  scale_fill_manual(values = condfillcolors_AxH) +
  new_scale_fill() + 
  geom_point(aes(color = Treatment, shape = Colony), size = 3, alpha = 0.8) +
  geom_point(size = 3, aes(fill = Treatment, shape = Colony), color = "black", stroke = 0.5, show.legend = FALSE) +
  scale_color_manual(values = condcolors_AxH) +
  scale_fill_manual(values = condcolors_AxH) +
  scale_shape_manual(values = colshapes, name="Colony") + 
  ylim(c(0,100)) +
  xlab(NULL) +
  ylab(NULL) +
  ggtitle("Bacteria Community Diversity") +
  theme(legend.position = "none",
          axis.text.x = element_text(angle = 0),
        strip.background = element_blank(),
        strip.text = element_blank())
```
```{r chao1_boxplot}
chao1 <- plot_richness(ps_assigned_AXH, x="Treatment", measures=c("Chao1")) +
  geom_boxplot(aes(fill = Treatment)) +
  scale_fill_manual(values = condfillcolors_AxH) +
  new_scale_fill() + 
  geom_point(aes(color = Treatment, shape = Colony), size = 3, alpha = 0.8) +
  geom_point(size = 3, aes(fill = Treatment, shape = Colony), color = "black", stroke = 0.5, show.legend = FALSE) +
  scale_color_manual(values = condcolors_AxH) +
  scale_fill_manual(values = condcolors_AxH) +
  scale_shape_manual(values = colshapes, name="Colony") + 
  scale_x_discrete(labels = c("C", "H", "A", "A.H")) +
  # ylim(c(0,20)) +
  xlab(NULL) +
  ylab("Chao1 ASV richness") +
  #ggtitle("Alpha diversity boxplot: Chao1 estimator") +
  theme(legend.position = "none",
          axis.text.x = element_text(angle = 0),
        strip.background = element_blank(),
        strip.text = element_blank())
chao1
# ggsave(chao1, filename = "./outputs/phyloseq-results/figures/chao1boxplot.pdf",  width = 50, height = 75, units = "mm", device = "pdf")
# ggsave(chao1, filename = "./manuscript_figures/Fig3B_chao1boxplot.pdf",  width = 50, height = 75, units = "mm", device = "pdf")
```
```{r shannon_boxplot}
shannon <- plot_richness(ps.AXH, x="Treatment", measures=c("Shannon")) +
 geom_boxplot(aes(fill = Treatment)) +
  scale_fill_manual(values = condfillcolors_AXH) +
  new_scale_fill() + 
  geom_point(aes(color = Treatment, shape = Colony), size = 3, alpha = 0.8) +
  geom_point(size = 3, aes(fill = Treatment, shape = Colony), color = "black", stroke = 0.5, show.legend = FALSE) +
  scale_color_manual(values = condcolors_AxH) +
  scale_fill_manual(values = condcolors_AxH) +
  scale_shape_manual(values = colshapes, name="Colony") + 
  scale_x_discrete(labels = c("C", "H", "A", "A+H")) +
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01), limits = c(0,4)) +
  xlab(NULL) +
  ylab("Shannnon diversity index") +
  theme(legend.position = "none",
          axis.text.x = element_text(angle = 0),
        strip.background = element_blank(),
        strip.text = element_blank())
shannon
```
```{r simpson_boxplot}
simpson <- plot_richness(ps.AXH, x="Treatment", measures=c("Simpson")) +
 geom_boxplot(aes(fill = Treatment)) +
  scale_fill_manual(values = condfillcolors_AXH) +
  new_scale_fill() + 
  geom_point(aes(color = Treatment, shape = Colony), size = 3, alpha = 0.8) +
  geom_point(size = 3, aes(fill = Treatment, shape = Colony), color = "black", stroke = 0.5, show.legend = FALSE) +
  scale_color_manual(values = condcolors_AxH) +
  scale_fill_manual(values = condcolors_AxH) +
  scale_shape_manual(values = colshapes, name="Colony") + 
  scale_x_discrete(labels = c("C", "H", "A", "A+H")) +
  ylim(c(0,1)) +
  xlab(NULL) +
  ylab("Simpson eveness index") +
  theme(legend.position = "none",
          axis.text.x = element_text(angle = 0),
        strip.background = element_blank(),
        strip.text = element_blank())
simpson
```
```{r}
richness_boxplots <- (chao1 | shannon | simpson)
richness_boxplots 
```

### Genotype-specific alpha diversity boxplots
```{r, message=FALSE, warning=FALSE}
alpha_geno <- function(ps = ps.AXH, alphameasure) {
alphabox <- plot_richness(ps, x = "Colony", measures = alphameasure) +
  geom_boxplot(aes(fill = Colony)) +
  geom_point(size = 3, aes(shape = Colony)) +
  scale_fill_manual(values = colcolors) +
  scale_shape_manual(values = colshapes)
print(alphabox)
}
for (alphameasure in alphameasures) {
  alpha_geno(ps.AXH, alphameasure)
}
```
Incorporate treatment separation
```{r, message=FALSE, warning=FALSE}
alpha_geno <- function(ps = ps.AXH, alphameasure) {
alphabox <- plot_richness(ps, x = "Colony", color = "Treatment", measures = alphameasure) +
  geom_boxplot(aes(fill = Colony)) +
  geom_point(size = 3, aes(shape = Colony)) +
  scale_color_manual(values = condcolors_AxH) +
  scale_fill_manual(values = colcolors) +
  scale_shape_manual(values = colshapes)
print(alphabox)
}
for (alphameasure in alphameasures) {
  alpha_geno(ps.AXH, alphameasure)
}
```

## Corrections needed 

### Statistical testing of alpha diversity differences
```{r}
# make a data frame from the sample_data
sampledf <- data.frame(sample_data(ps_filtered_AXH))
# 
ps_richness_meta <- left_join(ps_AXH_richness, sampledf, by = "SampleID")
```

```{r}
# Kruskal-Wallis testing for treatment effect
kruskal.test(data=ps_richness_meta, Observed ~ Treatment)
kruskal.test(data=ps_richness_meta, Chao1 ~ Treatment)
kruskal.test(data=ps_richness_meta, ACE ~ Treatment)
kruskal.test(data=ps_richness_meta, Shannon ~ Treatment)
kruskal.test(data=ps_richness_meta, Simpson ~ Treatment)
kruskal.test(data=ps_richness_meta, InvSimpson ~ Treatment)
kruskal.test(data=ps_richness_meta, Fisher ~ Treatment)
```

```{r}
# Kruskal-Wallis testing for reef effect
kruskal.test(data=ps_richness_meta, Observed ~ Reef)
kruskal.test(data=ps_richness_meta, Chao1 ~ Reef)
kruskal.test(data=ps_richness_meta, ACE ~ Reef)
kruskal.test(data=ps_richness_meta, Shannon ~ Reef)
kruskal.test(data=ps_richness_meta, Simpson ~ Reef)
kruskal.test(data=ps_richness_meta, InvSimpson ~ Reef)
kruskal.test(data=ps_richness_meta, Fisher ~ Reef)
```

```{r}
# Kruskal-Wallis testing for colony effect
kruskal.test(data=ps_richness_meta, Observed ~ Colony)
kruskal.test(data=ps_richness_meta, Chao1 ~ Colony)
kruskal.test(data=ps_richness_meta, ACE ~ Colony)
kruskal.test(data=ps_richness_meta, Shannon ~ Colony)
kruskal.test(data=ps_richness_meta, Simpson ~ Colony)
kruskal.test(data=ps_richness_meta, InvSimpson ~ Colony)
kruskal.test(data=ps_richness_meta, Fisher ~ Colony)
```

## Core microbiome
Coral core microbiome cutoffs: 50%, 80%, 90%, 100%

```{r}
ps.AXH.present <- prune_taxa(taxa_sums(ps.AXH) > 0, ps.AXH.rel)
ps.AXH.present
summarize_phyloseq(ps.AXH.present)
```
```{r}
datatable(otu_table(ps.AXH.present))
```
```{r}
core.taxa <- core_members(ps.AXH.present, detection = 0.001, prevalence = 80/100)
core.taxa
# Extract the taxonomy table
taxonomy.present <- as.data.frame(tax_table(ps.AXH.present))
# Subset this taxonomy table to include only core OTUs  
core_taxa_id <- subset(taxonomy.present, rownames(taxonomy.present) %in% core.taxa)
DT::datatable(core_taxa_id)
```

## Differential abundance testing
### ALDeX2
#### Heat
```{r}
# Treatment sample subsets of phyloseq objects
nsamples(ps_filtered_AXH)
samples <- sample_names(ps_filtered_AXH)
samples.HxC <- grep("[HW][wt][1-2].[46][abc]", samples, value = TRUE)
ps.HxC <- prune_samples(samples.HxC, ps_filtered_AXH)
ps.HxC
summarize_phyloseq(ps.HxC)
# Read out ASV tables from phyloseq objects
aldex.asv <- as.data.frame(t(otu_table(ps.HxC)))
```
```{r}
conds <- as.character(sample_data(ps.HxC)$Treatment)
conds <- factor(conds, levels = c("control", "Heat"), ordered = TRUE)
```
```{r}
x.ps <- aldex(reads = aldex.asv, conditions = conds, mc.samples = 128, test = "t", effect = TRUE, include.sample.summary = FALSE, denom = "all", verbose = TRUE)
```
```{r}
write.csv(x.ps, file = "./outputs/phyloseq-results/aldex2/anti-aldex2.csv")
```
```{r}
#pdf("./outputs/aldex2/anti-aldex2.pdf", height = 4, width = 8)
par(mfrow=c(1,2))
aldex.plot(x.ps, type="MW", test="welch", xlab="Dispersion", ylab="Difference")
aldex.plot(x.ps, type = "MA", test = "welch", xlab = "Log-ratio abundance", ylab = "Difference")

#dev.off()
```
```{r}
aldexmw <- aldex.plot_gg(x.ps, type = "MW", test = "welch")
aldexmw_heat <- aldexmw + 
  ggtitle("Heat vs. Control Treatment")
aldexma <- aldex.plot_gg(x.ps, type = "MA", test = "welch")
#aldex2 + ggtitle(subtitle = "Antibiotics + Heat vs. Control Treatment", "Bacteria ASV ALDeX2 Differential Abundance MA Plot") 
 
aldexplots <- (aldexmw | aldexma) 
aldexplots
ggsave(aldexplots, filename = "./outputs/phyloseq-results/aldex2/anti-asv-aldex2.pdf", width = 8, height = 4, units = "in", device = "pdf")
```
```{r}
cutoff <- 0.1
called <- x.ps[x.ps$we.eBH <= cutoff, ]
called.ASVs <- taxonomy[rownames(called), ]
called.ASVs1 <- cbind(called, called.ASVs)
```
```{r}
rare_cutoff <- 0
rare <- x.ps[x.ps$rab.all < rare_cutoff, ]
rare.ASVs <- taxonomy[rownames(rare), ]
rare.ASVs1 <- cbind(called, rare.ASVs)
```
#### Antibiotics
```{r}
# Treatment sample subsets of phyloseq objects
nsamples(ps_assigned)
samples <- sample_names(ps_assigned)
samples.AxC <- grep("[HW][wt][1-2].[16][abc]", samples, value = TRUE)
ps.AxC <- prune_samples(samples.AxC, ps_assigned)
ps.AxC
summarize_phyloseq(ps.AxC)
# Read out ASV tables from phyloseq objects
aldex.asv <- as.data.frame(t(otu_table(ps.AxC)))
```
```{r}
conds <- as.character(sample_data(ps.AxC)$Treatment)
conds <- factor(conds, levels = c("control", "Antibiotics.Heat"), ordered = TRUE)
```
```{r}
x.ps <- aldex(reads = aldex.asv, conditions = conds, mc.samples = 128, test = "t", effect = TRUE, include.sample.summary = FALSE, denom = "all", verbose = TRUE)
```
```{r}
write.csv(x.ps, file = "./outputs/phyloseq-results/aldex2/anti-aldex2.csv")
```
```{r}
#pdf("./outputs/aldex2/anti-aldex2.pdf", height = 4, width = 8)
par(mfrow=c(1,2))
aldex.plot(x.ps, type="MW", test="welch", xlab="Dispersion", ylab="Difference")
aldex.plot(x.ps, type = "MA", test = "welch", xlab = "Log-ratio abundance", ylab = "Difference")

#dev.off()
```
```{r}
aldexmw <- aldex.plot_gg(x.ps, type = "MW", test = "welch")
aldexmw_anti <- aldexmw + 
  ggtitle("Antibiotics vs. Control Treatment")
aldexma <- aldex.plot_gg(x.ps, type = "MA", test = "welch")
#aldex2 + ggtitle(subtitle = "Antibiotics + Heat vs. Control Treatment", "Bacteria ASV ALDeX2 Differential Abundance MA Plot") 
 
aldexplots <- (aldexmw | aldexma) 
aldexplots
ggsave(aldexplots, filename = "./outputs/phyloseq-results/figures/anti-asv-aldex2.pdf", width = 8, height = 4, units = "in", device = "pdf")
ggsave(aldexma, filename = "./outputs/phyloseq-results/figures/anti-asv-aldexma.pdf", width = 4, height = 3, units = "in", device = "pdf")
```
```{r}
cutoff <- 0.1
called <- x.ps[x.ps$we.eBH <= cutoff, ]
called.ASVs <- taxonomy[rownames(called), ]
called.ASVs1 <- cbind(called, called.ASVs)
```
```{r}
rare_cutoff <- 0
rare <- x.ps[x.ps$rab.all < rare_cutoff, ]
rare.ASVs <- taxonomy[rownames(rare), ]
rare.ASVs1 <- cbind(called, rare.ASVs)
```

## Examine specific taxa and within-taxa compositions
      filter_taxa
      prune_taxa
      subset_taxa
      
### Phylum-level subsets
```{r}
ps.AXH_proteobacteria <- subset_taxa(ps.AXH, Phylum=="D_1__Proteobacteria")
ps.AXH_cyanobacteria <- subset_taxa(ps.AXH, Phylum=="D_1__Cyanobacteria")
ps.AXH_bacteroidetes <- subset_taxa(ps.AXH, Phylum=="D_1__Bacteroidetes")
ps.AXH_actinobacteria <- subset_taxa(ps.AXH, Phylum=="D_1__Actinobacteria")
#datatable(tax_table(ps.AXH_cyanobacteria))
```
```{r}
glom_class <- tax_glom(ps.AXH_proteobacteria, taxrank = "Class")
ps.AXH_class <- psmelt(glom_class)
ps.AXH_class$Class <- as.character(ps.AXH_class$Class)
#ps.AXH_class <- filter(ps.AXH_class, Abundance > 0.005)
#ps.AXH_class$Class[ps.AXH_class$Abundance < 0.01] <- "<1% abundance"
ps.AXH_class$Sample <- factor(ps.AXH_class$Sample, levels = c("Hw1.6a", "Hw1.6b", "Hw1.6c", "Hw2.6a", "Hw2.6b", "Hw2.6c", "Wt1.6a", "Wt1.6b", "Wt1.6c", "Wt2.6a", "Wt2.6b", "Wt2.6c", "Hw1.3a", "Hw1.3b", "Hw1.3c", "Hw2.3a", "Hw2.3b", "Hw2.3c", "Wt1.3a", "Wt1.3b", "Wt1.3c", "Wt2.3a", "Wt2.3b", "Wt2.3c"))

colCount <- length(unique(ps.AXH_class$Class))
getPalette <- colorRampPalette(brewer.pal(9, "Set1"))
### all samples
p_class <- ggplot(data = ps.AXH_class, aes(x = Sample, y = Abundance, fill = Class))
p_class <- p_class +
  geom_bar(aes(), stat = "identity", position = "fill") +
  scale_fill_manual(values = getPalette(colCount)) +
  #guides(fill=guide_legend(nrow = 30)) +
  theme(axis.text.x = element_text(angle = 270))
p_class + ggtitle("Relative Abundance of Bacteria Classes (Phylum Proteobacteria)")

slices <- c(sum(ps.AXH_class$Abundance[ps.AXH_class$Class == "D_2__Alphaproteobacteria"]),
            sum(ps.AXH_class$Abundance[ps.AXH_class$Class == "D_2__Deltaproteobacteria"]),
            sum(ps.AXH_class$Abundance[ps.AXH_class$Class == "D_2__Gammaproteobacteria"]))
pct <- round((slices/sum(slices)*100), digits = 1)
lbls <- c("Alphaproteobacteria", "Deltaproteobacteria", "Gammaproteobacteria")
lbls <- paste(lbls, pct)
lbls <- paste(lbls, "%", sep="")
pie(slices, labels = lbls, col = getPalette(colCount))
```
Cyanobacteria dominated by Class Oxyphotobacteria
Bacteroidetes dominated by Class Bacteroidea

### Class-level subsets
```{r}
ps.AXH_alphaproteobacteria <- subset_taxa(ps.AXH_proteobacteria, Class=="D_2__Alphaproteobacteria")
ps.AXH_gammaproteobacteria <- subset_taxa(ps.AXH_proteobacteria, Class=="D_2__Gammaproteobacteria")
```

```{r}
ps.AXH_alphaproteobacteria <- transform_sample_counts(ps.AXH_alphaproteobacteria, function(x) {x / sum(x)} )
glom_order <- tax_glom(ps.AXH_alphaproteobacteria, taxrank = "Order")
ps.AXH_order <- psmelt(glom_order)
ps.AXH_order$Order <- as.character(ps.AXH_order$Order)
#ps.AXH_order <- filter(ps.AXH_order, Abundance > 0.005)
ps.AXH_order$Order[ps.AXH_order$Abundance < 0.05] <- "<5% abundance"
ps.AXH_order$Sample <- factor(ps.AXH_order$Sample, levels = c("Hw1.6a", "Hw1.6b", "Hw1.6c", "Hw2.6a", "Hw2.6b", "Hw2.6c", "Wt1.6a", "Wt1.6b", "Wt1.6c", "Wt2.6a", "Wt2.6b", "Wt2.6c", "Hw1.4a", "Hw1.4b", "Hw1.4c", "Hw2.4a", "Hw2.4b", "Hw2.4c", "Wt1.4a", "Wt1.4b", "Wt1.4c", "Wt2.4a", "Wt2.4b", "Hw1.5a", "Hw1.5b", "Hw1.5c", "Hw2.5a", "Hw2.5b", "Hw2.5c", "Wt1.5a", "Wt1.5b", "Wt1.5c", "Wt2.5a", "Wt2.5b", "Wt2.5c", "Hw1.1a", "Hw1.1b", "Hw1.1c", "Hw2.1a", "Hw2.1b", "Hw2.1c", "Wt1.1a", "Wt1.1b", "Wt1.1c", "Wt2.1a", "Wt2.1b", "Wt2.1c"), ordered = TRUE)

colCount <- length(unique(ps.AXH_order$Order))
getPalette <- colorRampPalette(brewer.pal(9, "Set1"))
### all samples
p_order <- ggplot(data = ps.AXH_order, aes(x = Sample, y = Abundance, fill = Order))
p_order <- p_order +
  geom_bar(aes(), stat = "identity", position = "fill") +
  scale_fill_manual(values = c("dark grey", getPalette(colCount))) +
  guides(fill=guide_legend(nrow = 30)) +
  theme(axis.text.x = element_text(angle = 270))
p_order
```

```{r}
slices <- c(sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "<5% abundance"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Caulobacterales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Rhizobiales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Rhodobacterales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Rhodospirillales"]))
pct <- round((slices/sum(slices)*100), digits = 1)
lbls <- c("<5% abundance", "Caulobacterales", "Rhizobiales", "Rhodobacterales", "Rhodospirillales")
lbls <- paste(lbls, pct)
lbls <- paste(lbls, "%", sep="")
pie(slices, labels = lbls, col = c("dark grey", getPalette(colCount)))
```
```{r}
ps.AXH_gammaproteobacteria <- transform_sample_counts(ps.AXH_gammaproteobacteria, function(x) {x / sum(x)} )
glom_order <- tax_glom(ps.AXH_gammaproteobacteria, taxrank = "Order")
ps.AXH_order <- psmelt(glom_order)
ps.AXH_order$Order <- as.character(ps.AXH_order$Order)
#ps.AXH_order <- filter(ps.AXH_order, Abundance > 0.005)
ps.AXH_order$Order[ps.AXH_order$Abundance < 0.01] <- "<1% abundance"
ps.AXH_order$Sample <- factor(ps.AXH_order$Sample <- factor(ps.AXH_order$Sample, levels = c("Hw1.6a", "Hw1.6b", "Hw1.6c", "Hw2.6a", "Hw2.6b", "Hw2.6c", "Wt1.6a", "Wt1.6b", "Wt1.6c", "Wt2.6a", "Wt2.6b", "Wt2.6c", "Hw1.4a", "Hw1.4b", "Hw1.4c", "Hw2.4a", "Hw2.4b", "Hw2.4c", "Wt1.4a", "Wt1.4b", "Wt1.4c", "Wt2.4a", "Wt2.4b", "Hw1.5a", "Hw1.5b", "Hw1.5c", "Hw2.5a", "Hw2.5b", "Hw2.5c", "Wt1.5a", "Wt1.5b", "Wt1.5c", "Wt2.5a", "Wt2.5b", "Wt2.5c", "Hw1.1a", "Hw1.1b", "Hw1.1c", "Hw2.1a", "Hw2.1b", "Hw2.1c", "Wt1.1a", "Wt1.1b", "Wt1.1c", "Wt2.1a", "Wt2.1b", "Wt2.1c"), ordered = TRUE))

colCount <- length(unique(ps.AXH_order$Order))
getPalette <- colorRampPalette(brewer.pal(9, "Set1"))
### all samples
p_order <- ggplot(data = ps.AXH_order, aes(x = Sample, y = Abundance, fill = Order))
p_order <- p_order +
  geom_bar(aes(), stat = "identity", position = "fill") +
  scale_fill_manual(values = c("dark grey", getPalette(colCount))) +
  guides(fill=guide_legend(nrow = 30)) +
  theme(axis.text.x = element_text(angle = 270))
p_order

```

```{r}
slices <- c(sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "<5% abundance"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Alteromonadales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Betaproteobacteriales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Cellvibrionales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Coxiellales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Francisellales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__JTB23"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__KI89A clade"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Oceanospirillales"]),
            sum(ps.AXH_order$Abundance[ps.AXH_order$Order == "D_3__Salinisphaerales"]))
pct <- round((slices/sum(slices)*100), digits = 1)
lbls <- c("<5% abundance", "Alteromonadales", "Betaproteobacteriales", "Cellvibrionales", "Coxiellales", "Francisellales", "JTB23", "KI89A clade", "Oceanospirillales", "Salinisphaerales")
lbls <- paste(lbls, pct)
lbls <- paste(lbls, "%", sep="")
pie(slices, labels = lbls, col = c("dark grey", getPalette(colCount)))
```

### Order-level subsets
Rhodobacterales
```{r}
ps.AXH_rhodobacterales <- subset_taxa(ps.AXH, Order=="D_3__Rhodobacterales")
ps.AXH_rhodobacterales
```
```{r}
ps.AXH_oceanospirillales <- subset_taxa(ps.AXH, Order=="D_3__Oceanospirillales")
ps.AXH_oceanospirillales
```

### Family-level subsets and data exploration
Endozoicomondaceae
```{r}
ps.AXH_endozoicomonadaceae <- subset_taxa(ps.AXH.rel, Family=="D_4__Endozoicomonadaceae")
ps.AXH_endozoicomonadaceae
summarize_phyloseq(ps.AXH_endozoicomonadaceae)
```

```{r}
#ps.AXH_endozoicomonadaceae <- transform_sample_counts(ps.AXH_endozoicomonadaceae, function(x) {x / sum(x)} )
glom_species <- tax_glom(ps.AXH_endozoicomonadaceae, taxrank = "Species")
ps.AXH_species <- psmelt(glom_species)
ps.AXH_species$Species <- as.character(ps.AXH_species$Species)
#ps.AXH_species <- filter(ps.AXH_species, Abundance > 0.001)
#ps.AXH_species$Species[ps.AXH_species$Abundance < 0.001] <- "<0.1% abundance"
###
colCount <- length(unique(ps.AXH_species$Species))
getPalette <- colorRampPalette(brewer.pal(9, "Set1"))
### all samples
p_species <- ggplot(data = ps.AXH_species, aes(x = Sample, y = Abundance, fill = Species))
p_species <- p_species +
  geom_bar(aes(), stat = "identity", position = "fill") +
  scale_fill_manual(values = getPalette(colCount)) +
  guides(fill=guide_legend(nrow = 30)) +
  theme(axis.text.x = element_text(angle = 270))
p_species
### samples collapsed into colonies
p_species <- ggplot(data = ps.AXH_species, aes(x = Treatment, y = Abundance, fill = Species))
p_species <- p_species +
  geom_bar(aes(), stat = "identity", position = "fill") +
  facet_grid(~Colony) +
  scale_fill_manual(values = getPalette(colCount)) +
  guides(fill=guide_legend(nrow = 30)) +
  theme(axis.text.x = element_text(angle = 270))
p_species
### samples collapsed into treatments
p_species <- ggplot(data = ps.AXH_species, aes(x = Treatment, y = Abundance, fill = Species))
p_species <- p_species +
  geom_bar(aes(), stat = "identity", position = "fill") +
  scale_fill_manual(values = getPalette(colCount)) +
  guides(fill=guide_legend(nrow = 30)) +
  theme(axis.text.x = element_text(angle = 270))
p_species
###
tree <- plot_tree(ps.AXH_endozoicomonadaceae, ladderize = TRUE, color = "Treatment", size = "Abundance") 
tree + scale_color_manual(values = condcolors)
```

Alteromonadaceae
```{r}
ps.AXH_alteromonadaceae <- subset_taxa(ps.AXH, Family=="D_4__Alteromonadaceae")
ps.AXH_alteromonadaceae
summarize_phyloseq(ps.AXH_alteromonadaceae)
```
```{r}
tree <- plot_tree(ps.AXH_alteromonadaceae, ladderize = TRUE, color = "Treatment", size = "Abundance") 
tree + scale_color_manual(values = condcolors)
```

### Genus-level subsets (Endozoicomonas)
Prevalence and relative abundance of Endozoicomonas across colonies, then treatments
```{r}
ps.AXH_endozoicomonas <- subset_taxa(ps.AXH, Genus=="D_5__Endozoicomonas")
ps.AXH_endozoicomonas
summarize_phyloseq(ps.AXH_endozoicomonas)
ps.AXH_endozoicomonas <- transform_sample_counts(ps.AXH_endozoicomonas, function(x) {x / sum(x)} )
```
```{r}
glom_endo <- tax_glom(ps.AXH_endozoicomonas, taxrank = "Genus")
ps.AXH_endo <- psmelt(glom_endo)
ps.AXH_endo$Genus <- as.character(ps.AXH_endo$Genus)
view(ps.AXH_endo)
```

```{r}
sum(ps.AXH_genus$Abundance[ps.AXH_genus$Genus=="D_5__Endozoicomonas"])/sum(ps.AXH_genus$Abundance)
```
```{r}
sum(ps.AXH_genus$Abundance[ps.AXH_genus$Genus=="D_5__Endozoicomonas" & ps.AXH_genus$Colony=="HW1"])/sum(ps.AXH_genus$Abundance[ps.AXH_genus$Colony=="HW1"])

sum(ps.AXH_genus$Abundance[ps.AXH_genus$Genus=="D_5__Endozoicomonas" & ps.AXH_genus$Colony=="HW2"])/sum(ps.AXH_genus$Abundance[ps.AXH_genus$Colony=="HW2"])

sum(ps.AXH_genus$Abundance[ps.AXH_genus$Genus=="D_5__Endozoicomonas" & ps.AXH_genus$Colony=="WT1"])/sum(ps.AXH_genus$Abundance[ps.AXH_genus$Colony=="WT1"])

sum(ps.AXH_genus$Abundance[ps.AXH_genus$Genus=="D_5__Endozoicomonas" & ps.AXH_genus$Colony=="WT2"])/sum(ps.AXH_genus$Abundance[ps.AXH_genus$Colony=="WT2"])
```

```{r}
relative_endo <- function(samp) {
rel <- sum(ps.AXH_genus$Abundance[ps.AXH_genus$Genus=="D_5__Endozoicomonas" & ps.AXH_genus$Sample==samp])/sum(ps.AXH_genus$Abundance[ps.AXH_genus$Sample==samp])
print(rel)
}
```
```{r}
samps <- c("Hw1.6a", "Hw1.6b", "Hw1.6c", "Hw2.6a", "Hw2.6b", "Hw2.6c", "Wt1.6a", "Wt1.6b", "Wt1.6c", "Wt2.6a", "Wt2.6b", "Wt2.6c", "Hw1.4a", "Hw1.4b", "Hw1.4c", "Hw2.4a", "Hw2.4b", "Hw2.4c", "Wt1.4a", "Wt1.4b", "Wt1.4c", "Wt2.4a", "Wt2.4b", "Hw1.5a", "Hw1.5b", "Hw1.5c", "Hw2.5a", "Hw2.5b", "Hw2.5c", "Wt1.5a", "Wt1.5b", "Wt1.5c", "Wt2.5a", "Wt2.5b", "Wt2.5c", "Hw1.1a", "Hw1.1b", "Hw1.1c", "Hw2.1a", "Hw2.1b", "Hw2.1c", "Wt1.1a", "Wt1.1b", "Wt1.1c", "Wt2.1a", "Wt2.1b", "Wt2.1c")
for (samp in samps){
relative_endo(samp)
}
```


## Phylogenetic trees
```{r}
actinobacteria_tree <- plot_tree(ps.AXH_actinobacteria,
                                  nodelabf = nodeplotboot(95, 0, 3),
                                  label.tips = "Genus",
                                  text.size = 3,
                                  size = "Abundance",
                                  color ="Treatment",
                                  ladderize = "left",
                                  base.spacing = 0.01,
                                  plot.margin = 0.4) 
actinobacteria_tree + 
  #coord_polar(theta = "y") +
  scale_color_manual(values = condcolors_AxH) +
  ggtitle("Phylum Actinobacteria")
```

```{r}
rhodobacterales_tree <- plot_tree(ps.AXH_rhodobacterales,
                                  nodelabf = nodeplotboot(95, 0, 3),
                                  label.tips = "Genus",
                                  text.size = 3,
                                  size = "Abundance",
                                  color ="Treatment",
                                  ladderize = "left",
                                  base.spacing = 0.01,
                                  plot.margin = 0.4) 
pdf("./outputs/phyloseq-results/figures/rhodobacterales_tree.pdf", width = 8, height = 2.5)
rhodobacterales_tree + 
  #coord_polar(theta = "y") +
  scale_color_manual(values = condcolors_AxH) +
  ggtitle("Order Rhodobacterales")
```
```{r}
oceanospirillales_tree <- plot_tree(ps.AXH_oceanospirillales,
                                  nodelabf = nodeplotboot(95, 0, 3),
                                  label.tips = "Genus",
                                  text.size = 3,
                                  size = "Abundance",
                                  color ="Treatment",
                                  ladderize = "left",
                                  base.spacing = 0.01,
                                  plot.margin = 0.4) 
pdf("./outputs/phyloseq-results/figures/oceanospirillales_tree.pdf", width = 8, height = 5)
oceanospirillales_tree + 
  #coord_polar(theta = "y") +
  scale_color_manual(values = condcolors_AxH) +
  ggtitle("Order Oceanospirillales")
```

```{r}
altermonadaceae_tree <- plot_tree(ps.AXH_alteromonadaceae,
                                  nodelabf = nodeplotboot(95, 0, 3),
                                  label.tips = "Genus",
                                  text.size = 3,
                                  size = "Abundance",
                                  color ="Treatment",
                                  ladderize = "left",
                                  base.spacing = 0.01,
                                  plot.margin = 0.4) 
pdf("./outputs/phyloseq-results/figures/alteromonadaceae_tree.pdf", width = 8, height = 4)
altermonadaceae_tree + 
  #coord_polar(theta = "y") +
  scale_color_manual(values = condcolors_AxH) +
  ggtitle("Family Alteromonadaceae")
```

## Microbial networks

## Summary
```{r}
sessionInfo()
```

