---
title: "Stable_DESeq-results_Pdam"
author: "Mike Connelly"
date: "10/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Setup packages and working directories
```{r packages, error=FALSE, warning=FALSE, message=FALSE}
library("tidyverse")
library("ggplot2")
library("ggrepel")
library("DESeq2")
```

Inspect results tables to determine number of significant up- and down-regulated genes 
      Significant DE genes a < 0.05
      lFC > 1
      lFC < -1
      Down
```{r, echo=FALSE}
      sum(res$padj<0.05, na.rm=TRUE)
      sum(res$padj<0.05 & res$log2FoldChange>=1, na.rm=TRUE)
      sum(res$padj<0.05 & res$log2FoldChange<=(-1), na.rm=TRUE)
```

##Create data frame with DEG info
```{r}
DEGdf <- data.frame(cbind(res$baseMean, res$log2FoldChange, res$pvalue, res$padj, res$IDGeneInfo))
colnames(DEGdf) <- c("baseMean", "log2FoldChange", "pvalue", "padj", "GeneInfo")
rownames(DEGdf) <- rownames(res)
DEGdf <- DEGdf[order(DEGdf$log2FoldChange, decreasing = TRUE),]
```
```{r}
write.csv(as.data.frame(DEGdf), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/alltreatments_res.csv")
```
##Obtain overall DEG table with Gene IDs
```{r}
#See results contrasts and gene commands markdowns for more info
ressig <- subset(res, padj<0.05)
ressig <- ressig[order(ressig$log2FoldChange, decreasing = TRUE),]
write.csv(as.data.frame(ressig), file="~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/alltreatments_res.csv")
```