---
title: "Stable_DESeq-contrasts_Pdam"
author: "Mike Connelly"
date: "10/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/computing/scripts/EAPSI.HW-WT-master/")
library(DESeq2)
```
```{r}
resultsNames(dds)
```

##Results contrasts between individual Treatments and control samples

### Antibiotics vs. Control
```{r}
res_anti_ctrl <- results(dds, contrast = c("Treatment", "Antibiotics", "control"))
res_anti_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti_ctrl$IDGeneInfo <- as.character(res_anti_ctrl$IDGeneInfo)
ressig_anti_ctrl <- subset(res_anti_ctrl, padj<0.1)
ressig_anti_ctrl_up <- subset(res_anti_ctrl, padj<0.1 & log2FoldChange>0.2)
ressig_anti_ctrl_dn <- subset(res_anti_ctrl, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti_ctrl[order(ressig_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti_ctrl.csv")
write.csv(as.data.frame(ressig_anti_ctrl_up[order(ressig_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti_ctrl_dn[order(ressig_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti_ctrl_dn.csv")
colnames(res_anti_ctrl)
summary(res_anti_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_ctrl_dn_ID.txt-e
```

### LPS vs. Control
```{r}
res_LPS_ctrl <- results(dds, contrast = c("Treatment", "LPS", "control"))
res_LPS_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_LPS_ctrl$IDGeneInfo <- as.character(res_LPS_ctrl$IDGeneInfo)
write.csv(as.data.frame(res_LPS_ctrl[order(res_LPS_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/all/res_LPS_ctrl.csv")
ressig_LPS_ctrl <- subset(res_LPS_ctrl, padj<0.1)
ressig_LPS_ctrl_up <- subset(res_LPS_ctrl, padj<0.1 & log2FoldChange>0.2)
ressig_LPS_ctrl_dn <- subset(res_LPS_ctrl, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_LPS_ctrl[order(ressig_LPS_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_LPS_ctrl.csv")
write.csv(as.data.frame(ressig_LPS_ctrl_up[order(ressig_LPS_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_LPS_ctrl_up.csv")
write.csv(as.data.frame(ressig_LPS_ctrl_dn[order(ressig_LPS_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_LPS_ctrl_dn.csv")
colnames(res_LPS_ctrl)
summary(res_LPS_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_LPS_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_LPS_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_LPS_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_LPS_ctrl_dn_ID.txt-e
```

### Heat vs. Control
```{r}
res_heat_ctrl <- results(dds, contrast = c("Treatment", "Heat", "control"))
res_heat_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_heat_ctrl$IDGeneInfo <- as.character(res_heat_ctrl$IDGeneInfo)
ressig_heat_ctrl <- subset(res_heat_ctrl, padj<0.1)
ressig_heat_ctrl_up <- subset(res_heat_ctrl, padj<0.1 & log2FoldChange>0.2)
ressig_heat_ctrl_dn <- subset(res_heat_ctrl, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_heat_ctrl[order(ressig_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_heat_ctrl.csv")
write.csv(as.data.frame(ressig_heat_ctrl_up[order(ressig_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_heat_ctrl_dn[order(ressig_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_heat_ctrl_dn.csv")
colnames(res_heat_ctrl)
summary(res_heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_heat_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_heat_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_heat_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_heat_ctrl_dn_ID.txt-e
```

### Antibiotics + Heat vs. Control
```{r}
res_anti.heat_ctrl <- results(dds, contrast = c("Treatment", "Antibiotics+Heat", "control"))
res_anti.heat_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat_ctrl$IDGeneInfo <- as.character(res_anti.heat_ctrl$IDGeneInfo)
ressig_anti.heat_ctrl <- subset(res_anti.heat_ctrl, padj<0.1)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_ctrl, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_ctrl, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat_ctrl_dn.csv")
colnames(res_anti.heat_ctrl)
summary(res_anti.heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_ctrl_dn_ID.txt-e
```

### Antibiotics + Heat + LPS vs. Control
```{r}
res_anti.heat.LPS_ctrl <- results(dds, contrast = c("Treatment", "Antibiotics+Heat+LPS", "control"))
res_anti.heat.LPS_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat.LPS_ctrl$IDGeneInfo <- as.character(res_anti.heat.LPS_ctrl$IDGeneInfo)
ressig_anti.heat.LPS_ctrl <- subset(res_anti.heat.LPS_ctrl, padj<0.1)
ressig_anti.heat.LPS_ctrl_up <- subset(res_anti.heat.LPS_ctrl, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat.LPS_ctrl_dn <- subset(res_anti.heat.LPS_ctrl, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat.LPS_ctrl[order(ressig_anti.heat.LPS_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_ctrl.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_ctrl_up[order(ressig_anti.heat.LPS_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_ctrl_dn[order(ressig_anti.heat.LPS_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_ctrl_dn.csv")
colnames(res_anti.heat.LPS_ctrl)
summary(res_anti.heat.LPS_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_ctrl_dn_ID.txt-e
```

### Antibiotics + Heat vs. Antibiotics
```{r}
res_anti.heat_anti <- results(dds, contrast = c("Treatment", "Antibiotics+Heat", "Antibiotics"))
res_anti.heat_anti$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat_anti$IDGeneInfo <- as.character(res_anti.heat_anti$IDGeneInfo)
ressig_anti.heat_anti <- subset(res_anti.heat_anti, padj<0.1)
ressig_anti.heat_anti_up <- subset(res_anti.heat_anti, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat_anti_dn <- subset(res_anti.heat_anti, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat_anti[order(ressig_anti.heat_anti$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat_anti.csv")
write.csv(as.data.frame(ressig_anti.heat_anti_up[order(ressig_anti.heat_anti_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat_anti_up.csv")
write.csv(as.data.frame(ressig_anti.heat_anti_dn[order(ressig_anti.heat_anti_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat_anti_dn.csv")
colnames(res_anti.heat_anti)
summary(res_anti.heat_anti)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat_anti.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat_anti_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat_anti_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_anti_dn_ID.txt-e
```

### Antibiotics + Heat vs. Heat
```{r}
res_anti.heat_heat <- results(dds, contrast = c("Treatment", "Antibiotics+Heat", "Heat"))
res_anti.heat_heat$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat_heat$IDGeneInfo <- as.character(res_anti.heat_heat$IDGeneInfo)
ressig_anti.heat_heat <- subset(res_anti.heat_heat, padj<0.1)
ressig_anti.heat_heat_up <- subset(res_anti.heat_heat, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat_heat_dn <- subset(res_anti.heat_heat, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat_heat[order(ressig_anti.heat_heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat_heat.csv")
write.csv(as.data.frame(ressig_anti.heat_heat_up[order(ressig_anti.heat_heat_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat_heat_up.csv")
write.csv(as.data.frame(ressig_anti.heat_heat_dn[order(ressig_anti.heat_heat_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat_heat_dn.csv")
colnames(res_anti.heat_heat)
summary(res_anti.heat_heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat_heat.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat_heat_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat_heat_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat_heat_dn_ID.txt-e
```

### Antibiotics + Heat + LPS vs. Antibiotics
```{r}
res_anti.heat.LPS_anti <- results(dds, contrast = c("Treatment", "Antibiotics+Heat+LPS", "Antibiotics"))
res_anti.heat.LPS_anti$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat.LPS_anti$IDGeneInfo <- as.character(res_anti.heat.LPS_anti$IDGeneInfo)
ressig_anti.heat.LPS_anti <- subset(res_anti.heat.LPS_anti, padj<0.1)
ressig_anti.heat.LPS_anti_up <- subset(res_anti.heat.LPS_anti, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat.LPS_anti_dn <- subset(res_anti.heat.LPS_anti, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat.LPS_anti[order(ressig_anti.heat.LPS_anti$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_anti.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_anti_up[order(ressig_anti.heat.LPS_anti_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_anti_up.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_anti_dn[order(ressig_anti.heat.LPS_anti_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_anti_dn.csv")
colnames(res_anti.heat.LPS_anti)
summary(res_anti.heat.LPS_anti)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_anti.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_anti_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_anti_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti_dn_ID.txt-e
```

### Antibiotics + Heat + LPS vs. Heat
```{r}
res_anti.heat.LPS_heat <- results(dds, contrast = c("Treatment", "Antibiotics+Heat+LPS", "Heat"))
res_anti.heat.LPS_heat$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat.LPS_heat$IDGeneInfo <- as.character(res_anti.heat.LPS_heat$IDGeneInfo)
ressig_anti.heat.LPS_heat <- subset(res_anti.heat.LPS_heat, padj<0.1)
ressig_anti.heat.LPS_heat_up <- subset(res_anti.heat.LPS_heat, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat.LPS_heat_dn <- subset(res_anti.heat.LPS_heat, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat.LPS_heat[order(ressig_anti.heat.LPS_heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_heat.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_heat_up[order(ressig_anti.heat.LPS_heat_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_heat_up.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_heat_dn[order(ressig_anti.heat.LPS_heat_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_heat_dn.csv")
colnames(res_anti.heat.LPS_heat)
summary(res_anti.heat.LPS_heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_heat.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_heat_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_heat_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_heat_dn_ID.txt-e
```

### Antibiotics + Heat + LPS vs. LPS
```{r}
res_anti.heat.LPS_LPS <- results(dds, contrast = c("Treatment", "Antibiotics+Heat+LPS", "LPS"))
res_anti.heat.LPS_LPS$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat.LPS_LPS$IDGeneInfo <- as.character(res_anti.heat.LPS_LPS$IDGeneInfo)
ressig_anti.heat.LPS_LPS <- subset(res_anti.heat.LPS_LPS, padj<0.1)
ressig_anti.heat.LPS_LPS_up <- subset(res_anti.heat.LPS_LPS, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat.LPS_LPS_dn <- subset(res_anti.heat.LPS_LPS, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat.LPS_LPS[order(ressig_anti.heat.LPS_LPS$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_LPS.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_LPS_up[order(ressig_anti.heat.LPS_LPS_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_LPS_up.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_LPS_dn[order(ressig_anti.heat.LPS_LPS_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_LPS_dn.csv")
colnames(res_anti.heat.LPS_LPS)
summary(res_anti.heat.LPS_LPS)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_LPS.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_LPS_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_LPS_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_LPS_dn_ID.txt-e
```

### Antibiotics + Heat + LPS vs. Antibiotics + Heat
```{r}
res_anti.heat.LPS_anti.heat <- results(dds, contrast = c("Treatment", "Antibiotics+Heat+LPS", "Antibiotics+Heat"))
res_anti.heat.LPS_anti.heat$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat.LPS_anti.heat$IDGeneInfo <- as.character(res_anti.heat.LPS_anti.heat$IDGeneInfo)
ressig_anti.heat.LPS_anti.heat <- subset(res_anti.heat.LPS_anti.heat, padj<0.1)
ressig_anti.heat.LPS_anti.heat_up <- subset(res_anti.heat.LPS_anti.heat, padj<0.1 & log2FoldChange>0.2)
ressig_anti.heat.LPS_anti.heat_dn <- subset(res_anti.heat.LPS_anti.heat, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti.heat.LPS_anti.heat[order(ressig_anti.heat.LPS_anti.heat$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_anti.heat.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_anti.heat_up[order(ressig_anti.heat.LPS_anti.heat_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_anti.heat_up.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_anti.heat_dn[order(ressig_anti.heat.LPS_anti.heat_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_anti.heat_dn.csv")
colnames(res_anti.heat.LPS_anti.heat)
summary(res_anti.heat.LPS_anti.heat)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti.heat.LPS_anti.heat.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti.heat.LPS_anti.heat_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti.heat.LPS_anti.heat_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti.heat.LPS_anti.heat_dn_ID.txt-e
```

### Antibiotics vs. LPS
```{r}
res_anti_LPS <- results(dds, contrast = c("Treatment", "Antibiotics", "LPS"))
res_anti_LPS$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti_LPS$IDGeneInfo <- as.character(res_anti_LPS$IDGeneInfo)
ressig_anti_LPS <- subset(res_anti_LPS, padj<0.1)
ressig_anti_LPS_up <- subset(res_anti_LPS, padj<0.1 & log2FoldChange>0.2)
ressig_anti_LPS_dn <- subset(res_anti_LPS, padj<0.1 & log2FoldChange<0.2)
write.csv(as.data.frame(ressig_anti_LPS[order(ressig_anti_LPS$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti_LPS.csv")
write.csv(as.data.frame(ressig_anti_LPS_up[order(ressig_anti_LPS_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti_LPS_up.csv")
write.csv(as.data.frame(ressig_anti_LPS_dn[order(ressig_anti_LPS_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti_LPS_dn.csv")
colnames(res_anti_LPS)
summary(res_anti_LPS)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/overall/res_anti_LPS.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/up/res_anti_LPS_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/tables/down/res_anti_LPS_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_Pdam/lists/res_anti_LPS_dn_ID.txt-e
```
